---
title: "covid_conspiracies_markdown2"
author: "Michael Marshall"
date: "21/10/2020"
output: github_document
---

## Loading Packages and Data

```{r, message = FALSE, warnings = FALSE}
pacman::p_load(tidyverse, stringr, ggridges, forcats, labelled, leaps,
               psych, corrr, cowplot, expss, haven, interplot,
               interactions, jtools,labelled, pscl, psych, 
               sjPlot, skimr)

load("COVID W1_W2_W3 Cleaned 2878.RData") # needs to be in your wd
```

## Rescaling variable

```{r}
## [rescale01] Function to rescale a variable from 0 to 1
rescale01 <- function(x, ...) {
  (x - min(x, ...)) / ((max(x, ...)) - min(x, ...))
}
```

## Summary and distribution of different COVID specific conspiracies

```{r, message = FALSE, warning = FALSE}
# plotting density of different covid conspiracies
df %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  gather(conspiracy_code, belief,
         W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>%
  mutate(conspiracy_code = as.factor(conspiracy_code)) %>%
  filter(!conspiracy_code %in% c("W2_Conspiracy_Theory4",
                                 "W2_Conspiracy_Theory5")) %>% 
  ggplot(aes(x = belief, y = conspiracy_code, height = ..density..)) +
  geom_density_ridges(aes(rel_min_height = 0.005),
                      stat = "density",
                      fill = get_colors("CUD Bright",num.colors = 1)) +
  theme_nice() +
  scale_y_discrete(labels = c("Wuhan laboratory","Meat market","5G")) +
  labs(y = NULL, x = "Belief scale (0-100)",
       caption = "Distribution of origin theory belief") +
  theme(plot.caption = element_text(hjust = 0.61,
                                    face = "bold",
                                    size = 10),
        axis.title.x = element_text(size = 8,
                                    hjust = 0.5)
  )
```

```{r}
#pacman::p_load(patchwork)
df %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  gather(conspiracy_code, belief,
         W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>%
  mutate(conspiracy_code = fct_recode(
    as.factor(conspiracy_code),
    "Wuhan laboratory" = "W2_Conspiracy_Theory1",
    "Meat market" = "W2_Conspiracy_Theory2",
    "5G" = "W2_Conspiracy_Theory3",
    "4" = "W2_Conspiracy_Theory4",
    "5" = "W2_Conspiracy_Theory5")
    ) %>%
  filter(!conspiracy_code %in% c("4","5")) %>% 
  mutate(
    order_var = ifelse(conspiracy_code == "Meat market", 1,
                       ifelse(conspiracy_code == "Wuhan laboratory",2,3))
  ) %>% 
  ggplot(aes(x = belief)) +
  geom_density(fill = get_colors("CUD Bright",num.colors = 1),
               alpha = 0.8) +
  theme_nice() +
  facet_wrap(~fct_reorder(conspiracy_code,order_var), 
             scales = "free_y", ncol = 1) +
  labs(y = "Density", 
       x = "Distribution of origin theory belief")
```


## Cleaning dataset

The following code filters down to just those observations that have completed the battery of questions relating to COVID specific conspiracies.  It also creates a tibble counting the missing observations, which can be useful to have as an object.  

```{r}
# filtering for completed dependent variable
conspiracies <- df %>% 
  filter(!is.na(W2_Conspiracy_Theory1) |
           !is.na(W2_Conspiracy_Theory2) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory4) |
           !is.na(W2_Conspiracy_Theory5)) %>% 
  rename(W1_Housing_tenure = W1_Hosuing_tenure)

# function to count NAs
count_na <- function(x){
  sum(is.na(x))
}

conspiracies %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  map_int(count_na)

missing <- tibble(
  variable = names(conspiracies),
  NAs = conspiracies %>% map_int(count_na)
)

#View(missing)
```

The code below combines the two variables on the 2019 general election into a single variable that combines whether a respondent voted, and who they voted for.  It also turns the *preferred newspaper* variables into dummy variables, as they were previously coded as *1=Yes* and everything else as *NA*.  

```{r}

# making preferred newspaper dummy variable (i.e. replacing NA with 0)
na_to_zero <- function(x){
  x[is.na(x)] <- 0
  x <- as.numeric(x)
  return(x)
} 

paper_vars <- rep(str_c("W2_Newspaper_prefer",seq(1,11,1)))

conspiracies[paper_vars] <- conspiracies[paper_vars] %>% 
  map_df(na_to_zero)

conspiracies <- conspiracies %>% 
  mutate(
    red_top_tabloid = ifelse(
      W2_Newspaper_prefer3 == 1 | W2_Newspaper_prefer2 == 1 |
        W2_Newspaper_prefer7 == 1 | W2_Newspaper_prefer8 == 1 |
        W2_Newspaper_prefer9 == 1, 1, 0),
    mid_level_news = ifelse(
      W2_Newspaper_prefer1 == 1 | W2_Newspaper_prefer4 == 1, 1, 0),
    elite_news = ifelse(
      W2_Newspaper_prefer5 == 1 | W2_Newspaper_prefer6 == 1 |
        W2_Newspaper_prefer10 == 1 | 
        W2_Newspaper_prefer11 == 1, 1, 0)
  )

conspiracies %>% 
  count(red_top_tabloid, mid_level_news, elite_news)
```

```{r}
# Creating DVs
# [nat] nationalism
nat_keys <- list(nationalism = cs(W2_Nationalism1,W2_Nationalism2))
nat_test <- scoreItems(nat_keys, conspiracies, min = 1, max = 5)
head(nat_test$scores)
nat_test$alpha  # Scale alpha
conspiracies$nat <- rescale01(nat_test$scores, na.rm = TRUE)
conspiracies$nat <- c(conspiracies$nat)  # Ensure variable is numeric and not matrix class
describe(conspiracies$nat)
```

```{r}
## [imm.econ] Anti-immigrant sentiment - Economy 
table(conspiracies$W1_MigrantAttitudes1)
conspiracies$imm_econ <- rescale01(abs(
  conspiracies$W1_MigrantAttitudes1 - 11))

conspiracies %>% 
  dplyr::select(W1_MigrantAttitudes1, imm_econ) %>%
  correlate()

## [imm.res] Anti-immigrant sentiment - Resources
table(conspiracies$W1_MigrantAttitudes3)
conspiracies$imm_res <- rescale01(conspiracies$W1_MigrantAttitudes3)
conspiracies %>% 
  dplyr::select(W1_MigrantAttitudes3, imm_res) %>%
  correlate()

## [imm.cul] Anti-immigrant sentiment - Culture
table(conspiracies$W1_MigrantAttitudes2)
conspiracies$imm_cul <- rescale01(abs(
  conspiracies$W1_MigrantAttitudes2 - 11))

conspiracies %>% 
  dplyr::select(W1_MigrantAttitudes2, imm_cul) %>%
  correlate()
```

```{r}
# Right wing authoritarianism
rwa_keys <- list(rwa = cs(W1_Authoritarianism1_R,
                          W1_Authoritarianism2,
                          W1_Authoritarianism3,
                          W1_Authoritarianism4_R, 
                          W1_Authoritarianism5_R,
                          W1_Authoritarianism6))

rwa_test <- scoreItems(rwa_keys, conspiracies, min = 1, max = 5)
head(rwa_test$scores)
summary(rwa_test$alpha)  # Scale alpha
conspiracies$RWA <- rescale01(rwa_test$scores, na.rm = TRUE)
conspiracies$RWA <- c(conspiracies$RWA)  # Ensure variable is numeric and not matrix class

describe(conspiracies$RWA)
```

```{r}
## [SDO] Social Dominance Orientation
sdo_keys <- list(sdo = cs(W1_Social_Dominance1,
                          W1_Social_Dominance2_R,
                          W1_Social_Dominance3_R,
                          W1_Social_Dominance4,
                          W1_Social_Dominance5_R,
                          W1_Social_Dominance6, 
                          W1_Social_Dominance7,
                          W1_Social_Dominance8_R))
sdo_test <- scoreItems(sdo_keys, conspiracies, min = 1, max = 5)
head(sdo_test$scores)
summary(sdo_test$alpha)  # Scale alpha
conspiracies$SDO <- rescale01(sdo_test$scores, na.rm = TRUE)
conspiracies$SDO <- c(conspiracies$SDO)  # Ensure variable is numeric and not matrix class

summary(conspiracies$SDO)
```

```{r}
## [threat] Covid-19 related Threat
summary(conspiracies$W2_COVID19_anxiety)
conspiracies$threat <- rescale01(conspiracies$W2_COVID19_anxiety)
conspiracies %>% 
  dplyr::select(W2_COVID19_anxiety, threat) %>%
  correlate()
```

```{r}
## [right] Right-Wing political views
table(conspiracies$W1_Political_Scale)
conspiracies$right <- rescale01(conspiracies$W1_Political_Scale)
conspiracies %>% 
  dplyr::select(W1_Political_Scale, right) %>%
  correlate()
```

```{r}
## [soc.con] Social conservatism
table(conspiracies$W1_Political_Abortion_SSM)
conspiracies$soc_con <- rescale01(
  conspiracies$W1_Political_Abortion_SSM)
conspiracies %>% 
  dplyr::select(W1_Political_Abortion_SSM, soc_con) %>%
  correlate()
```

```{r}
## [fis.con] Fiscal conservatism
table(conspiracies$W1_Political_Fiscal)
conspiracies$fis_con <- rescale01(conspiracies$W1_Political_Fiscal)
conspiracies %>% 
  dplyr::select(W1_Political_Fiscal, fis_con) %>%
  correlate()
```

```{r}
## [age.c] Age (in years)
summary(conspiracies$W2_Age_year)
conspiracies$age_sc <- rescale01(conspiracies$W2_Age_year)
```

```{r}
# conspiracy ideation alpha
consp_keys <- list(consp = cs(W1_Conspiracy_1,
                          W1_Conspiracy_2,
                          W1_Conspiracy_3,
                          W1_Conspiracy_4,
                          W1_Conspiracy_5))
consp_test <- scoreItems(consp_keys, conspiracies, min = 1, max = 11)
head(consp_test$scores)
consp_test$alpha  # Scale alpha

cor(consp_test$scores, conspiracies$W1_Conspiracy_Total)
```

```{r}
# conspiracy ideation alpha
iou_keys <- list(iou = cs(W2_IOU1, W2_IOU2,W2_IOU3, W2_IOU4,
                          W2_IOU5, W2_IOU5,W2_IOU6,W2_IOU7,
                          W2_IOU7,W2_IOU8,W2_IOU9,W2_IOU10,
                          W2_IOU11,W2_IOU12))
iou_test <- scoreItems(iou_keys, conspiracies, min = 1, max = 5)
head(iou_test$scores)
iou_test$alpha  # Scale alpha

cor(iou_test$scores, conspiracies$W2_IOU_Total)
```

```{r}
# conspiracy ideation alpha
chance_keys <- list(chance = cs(W2_LOC1,
                                W2_LOC3,
                                W2_LOC9))
chance_test <- scoreItems(chance_keys, conspiracies, min = 1, max = 7)
head(chance_test$scores)
chance_test$alpha  # Scale alpha

cor(chance_test$scores, conspiracies$W2_Chance_Total)
```

```{r}
# conspiracy ideation alpha
int_keys <- list(int = cs(W2_LOC5,
                          W2_LOC6,
                          W2_LOC8))
int_test <- scoreItems(int_keys, conspiracies, min = 1, max = 7)
head(int_test$scores)
int_test$alpha  # Scale alpha

cor(int_test$scores, conspiracies$W2_Internal_Total)
```

```{r}
# conspiracy ideation alpha
po_keys <- list(po = cs(W2_LOC2,
                        W2_LOC4,
                        W2_LOC7))
po_test <- scoreItems(po_keys, conspiracies, min = 1, max = 7)
head(po_test$scores)
po_test$alpha  # Scale alpha

cor(po_test$scores, conspiracies$W2_PO_Total)

ggplot(data = NULL, aes(x = po_test$scores,
                        conspiracies$W2_PO_Total)) +
  geom_point(alpha = 1/3)

```

```{r}
# paranoia alpha
par_keys <- list(par = cs(W2_Paranoia1,
                        W2_Paranoia2,
                        W2_Paranoia3, W2_Paranoia4, W2_Paranoia5))
par_test <- scoreItems(par_keys, conspiracies, min = 1, max = 5)
head(par_test$scores)
par_test$alpha  # Scale alpha

cor(par_test$scores, conspiracies$W2_Paranoia_Total)
```

```{r}
# dai alpha
dai_keys <- list(dai = cs(W2_DAI1,W2_DAI2,W2_DAI3,W2_DAI4,W2_DAI5,
                        W2_DAI6,W2_DAI7,W2_DAI8,W2_DAI9,W2_DAI10,
                        W2_DAI11, W2_DAI12, W2_DAI13,W2_DAI14,
                        W2_DAI15,W2_DAI16,W2_DAI17))
dai_test <- scoreItems(dai_keys, conspiracies, min = 1, max = 5)
head(dai_test$scores)
dai_test$alpha  # Scale alpha

cor(dai_test$scores, conspiracies$W2_DAI_Total)
```


```{r}
factors <- c("W1_Ethnicity","W1_C19_Infected","W1_BornUK","W1_EURef",
             "W2_Gender_binary","W2_Living_alone","W2_Employment",
             "W1_Education_binary","W1_Housing_tenure")
```

```{r}
# turning the above list into factors with the levels as the spss labels
#for(i in seq_along(conspiracies[factors])){
#  conspiracies[factors][,i] <- to_factor(
#    conspiracies[factors][,i], nolabel_to_na = TRUE)
#}
```

```{r}
# turning to factors
conspiracies[factors] <- conspiracies[factors] %>% 
  map_df(as.factor)
```

```{r}
# Making a binary for each CRT scale, baseline = incorrect answer
conspiracies$CRT1 <- ifelse(
  to_factor(conspiracies$W1_CRT1) == "5 pence", 1, 0
)

conspiracies$CRT2 <- ifelse(
  to_factor(conspiracies$W1_CRT2) == "5 minutes", 1, 0
)

conspiracies$CRT3 <- ifelse(
  to_factor(conspiracies$W1_CRT3) == "47 days", 1, 0
)

conspiracies$CRT4 <- ifelse(
  to_factor(conspiracies$W1_CRT4) == "2nd", 1, 0
)

conspiracies$CRT5 <- ifelse(
  to_factor(conspiracies$W1_CRT5) == "8", 1, 0
)

conspiracies$CRT_test <- ifelse(
  to_factor(conspiracies$W1_CRT_test) == "None of them.", 1, 0
) # baseline = heard of some of them OR all of them
```

```{r}
# CRT
crt_keys <- list(crt = cs(CRT1,
                          CRT2,
                          CRT3,
                          CRT4, 
                          CRT5
                          ))

crt_test <- scoreItems(crt_keys, conspiracies, min = 0, max = 1)
head(crt_test$scores)
summary(crt_test$alpha)  # Scale alpha
conspiracies$crt <- rescale01(crt_test$scores, na.rm = TRUE)
conspiracies$crt <- c(conspiracies$crt)  # Ensure variable is numeric and not matrix class

describe(conspiracies$crt)
```


```{r}
# do CRT scores come from different distributions
# dependent on whether they've seen the test

conspiracies %>% 
  group_by(CRT_test) %>% 
  summarise(
    mean_crt = mean(crt),
    median_crt = median(crt),
    std_crt = sd(crt)
  )

kruskal.test(crt ~ CRT_test, data = conspiracies)
```

```{r}
# renaming trust in science
conspiracies <- conspiracies %>% 
  rename(distrust_science = W2_Trust_Body6)
```


```{r}
# rescaling the remaing numeric variables
numerics <- c("W1_Conspiracy_Total","W2_Paranoia_Total",
              "W2_Internal_Total","W2_Chance_Total","W2_PO_Total",
              "W2_DAI_Total","W2_IOU_Total", "W2_INFO_5",
              "W2_INFO_9","distrust_science","W1_Income_2019")

conspiracies[numerics] <- conspiracies[numerics] %>% 
  map_df(rescale01, na.rm = TRUE)
```


```{r}
# creating scaled versions of each conspiracy belief
conspiracies$conspiracy1_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory1, na.rm = TRUE
)

conspiracies$conspiracy2_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory2, na.rm = TRUE
)

conspiracies$conspiracy3_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory3, na.rm = TRUE
)

conspiracies$conspiracy4_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory4, na.rm = TRUE
)

conspiracies$conspiracy5_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory5, na.rm = TRUE
)
```


## Distribution of variables

A for loop to look at distribution of potential independent variables (numeric only).  

```{r}
plot_vars <- conspiracies %>% 
  dplyr::select(
    one_of(numerics),nat,RWA,SDO,threat,right,soc_con,fis_con
    ) %>%
  names()

for(i in seq_along(plot_vars)){
  
  x1 <- conspiracies[plot_vars][i] %>% as_vector()
  
  print(
    ggplot(data = NULL, aes(x = x1)) +
      geom_vline(aes(xintercept = mean(x1, na.rm =TRUE)), 
                 colour = "black",
                 linetype = "dashed") +
      geom_vline(aes(xintercept = median(x1, na.rm =TRUE)), 
                 colour = "red",
                 linetype = "dashed") +
      geom_density(fill = "lightblue", alpha = 0.7) +
      labs(x = plot_vars[i],
           caption = "Black = Mean, Red = Median")  
  )
  
}
```


# Principal Components Analysis - PCA

```{r}
# pca on conspiracy theory variables
pca_df <- conspiracies %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5)

pca_fit <- prcomp(pca_df,scale = TRUE)
```

```{r}
# looking at biplots for components 1:4
biplot(pca_fit,
       col = c("lightgrey","red"))

biplot(pca_fit, choices = 3:4,
       col = c("lightgrey","red"))

pca_fit$rotation[,1:4]

components <- pca_fit$x[,1:4] %>% as_tibble()
```

First four principal components are as follows:  
1. general conspiracy ideation, with belief in 5G, 'it's no worse than flu' and vitamin C treatment highly loaded to this component, and belief in Chinese lab less so  
2. disbelief in Chinese meat market origin, with mild positive loading for Chinese lab origin  
3. strong conspiracy ideation (non-nationalistic), strong loading for belig 5g, 'it's no worse than flu' and vitamin C treatment, with negative loading for both Chinese lab origin and Chinese meat market  
4. strong loading for belief in 5G conspiracy and vitamin C treatment, but strong negative loading for belief 'it's no worse than flu'  


```{r}
pc <- cbind(conspiracies,components)

pc <- pc %>% 
  mutate(
    pc1_ihs = asinh(PC1)
  )

pc %>% 
  ggplot(aes(x = pc1_ihs)) +
  geom_density() +
  labs(x = "Principal Component 1 (IHS)")

pc %>% 
  ggplot(aes(x = PC2)) +
  geom_density() +
  labs(x = "Principal Component 2")

pc %>% 
  ggplot(aes(x = PC3)) +
  geom_density() +
  labs(x = "Principal Component 3")

pc %>% 
  ggplot(aes(x = PC4)) +
  geom_density()  +
  labs(x = "Principal Component 4")
```

Principal components 1 to 3 explain most of the variation in the data.  

```{r}
# modelling principal components against general conspiracy ideation
conspiracy_mod <- lm(W1_Conspiracy_Total ~ pc1_ihs + PC2 + PC3 + PC4,
                     data = pc)

par(mfrow = c(2,2))
plot(conspiracy_mod)

summ(conspiracy_mod, vifs = TRUE)

source("diagnostic_plots.R")
```

Only principal components 1 and 3 associated with general conspiracy ideation.  


# Modelling for belief in Chinese lab origin

## DV Chinese lab conspiracy - singular IV models

```{r}
sdo_lab <- lm(conspiracy1_sc ~ SDO,
              data = conspiracies)

summ(sdo_lab)
```

```{r}
rwa_lab <- lm(conspiracy1_sc ~ RWA,
              data = conspiracies)

summ(rwa_lab)
```

```{r}
mid_news_lab <- lm(conspiracy1_sc ~ mid_level_news,
              data = conspiracies)

summ(mid_news_lab)
```

```{r}
social_m_lab <- lm(conspiracy1_sc ~ W2_INFO_5,
              data = conspiracies)

summ(social_m_lab)
```

## DV Chinese lab conspiracy - socio-economic variables

```{r}
se_lab <- lm(conspiracy1_sc ~ W2_Gender_binary +
               W1_Education_binary +
               W1_Income_2019 +
               age_sc,
              data = conspiracies)

summ(se_lab, vifs = TRUE)
```

## DV Chinese lab conspiracy - socio-economic variables + political/media

```{r}
se_pol_lab <- lm(conspiracy1_sc ~ 
                   
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   right +
                   soc_con +
                   fis_con +
                   nat +
                   distrust_science + #distrust of scientists
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news + 
                   W2_INFO_5 + #social media
                   W2_INFO_9, #family and friends
                 data = conspiracies)

summ(se_pol_lab, vifs = TRUE)
```

```{r}
AIC(se_lab)
AIC(se_pol_lab)
```


## DV Chinese lab conspiracy - socio-economic variables + political/media + pol-psych

```{r}
se_polpsych_lab <- lm(conspiracy1_sc ~
                        
                        #socio-economic variables
                        W2_Gender_binary +
                        W1_Education_binary +
                        W1_Income_2019 +
                        age_sc +
                        
                        #political and media variables
                        right +
                        soc_con +
                        fis_con +
                        nat +
                        distrust_science + #distrust of scientists
                        red_top_tabloid + 
                        mid_level_news + 
                        elite_news + 
                        W2_INFO_5 + #social media
                        W2_INFO_9 + #family and friends
                     
                        #political-psychology variables
                        SDO +
                        RWA +
                        W2_DAI_Total +
                        W2_IOU_Total +
                        W2_Paranoia_Total +
                        W2_Internal_Total +
                        W2_Chance_Total +
                        W2_PO_Total,
                      data = conspiracies)

summ(se_polpsych_lab, vifs = TRUE)
```

Looking at mulitcollinearity below for the following variables: 

* right  
* soc_con  
* fis_con  
* paranoia  

```{r}
# looking for potential multicollinearity with right
cor_mat <- model.matrix(se_polpsych_lab) %>% as.data.frame()

cor_vec <- rep(NA,ncol(cor_mat))
for(i in seq_along(cor_mat)){
  cor_vec[i] <- cor(cor_mat$right,cor_mat[,i])
}

tibble(cor_vec,
       names(cor_mat)) %>% 
  arrange(desc(cor_vec))
```

Fiscal conservatism positively correlated with right-left scale.  

```{r}
# looking for multicollinearity with soc_con
cor_vec2 <- rep(NA,ncol(cor_mat))
for(i in seq_along(cor_mat)){
  cor_vec2[i] <- cor(cor_mat$soc_con,cor_mat[,i])
}

tibble(cor_vec2,
       names(cor_mat)) %>% 
  arrange(desc(cor_vec2))
```

Fiscal conservatism, right-wing scale and RWA correlated with soc_con.  

```{r}
# looking for multicollinearity with fis_con
cor_vec3 <- rep(NA,ncol(cor_mat))
for(i in seq_along(cor_mat)){
  cor_vec3[i] <- cor(cor_mat$fis_con,cor_mat[,i])
}

tibble(cor_vec3,
       names(cor_mat)) %>% 
  arrange(desc(cor_vec3))
```

Right, soc_con correlated with fis_con.  

```{r}
# looking for multicollinearity with paranoia
cor_vec4 <- rep(NA,ncol(cor_mat))
for(i in seq_along(cor_mat)){
  cor_vec4[i] <- cor(cor_mat$W2_Paranoia_Total,cor_mat[,i])
}

tibble(cor_vec4,
       names(cor_mat)) %>% 
  arrange(desc(cor_vec4))
```

Potential multicollinearity between right, soc_con and fis_con. From hereon, fis_con is included in the models, as of the three, it shows the least positive correlation between SDO and RWA.  In addition, the variables relating to locus of control (W2_Internal_Total, W2_Chance_Total) are dropped due to non-significance.  

## DV Chinese lab belief - model above minus the aforementioned variables

```{r}
se_polpsych_lab_2 <- lm(conspiracy1_sc ~
                        
                        #socio-economic variables
                        W2_Gender_binary +
                        W1_Education_binary +
                        W1_Income_2019 +
                        age_sc +
                        
                        #political and media variables
                        fis_con +
                        nat +
                        distrust_science + #distrust of scientists
                        red_top_tabloid + 
                        mid_level_news + 
                        elite_news + 
                        W2_INFO_5 + #social media
                        W2_INFO_9 + #family and friends
                     
                        #political-psychology variables
                        SDO +
                        RWA +
                        W2_DAI_Total +
                        W2_IOU_Total +
                        W2_Paranoia_Total,
                      data = conspiracies)

summ(se_polpsych_lab_2, vifs = TRUE)
```

```{r}
AIC(se_pol_lab)
AIC(se_polpsych_lab_2)
```


## DV Chinese lab conspiracy - socio-economic variables + political/media + pol-psych + covid-threat + CRT

```{r}
multi_lab <- lm(conspiracy1_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  
                  #covid-anxety
                  threat +
                  
                  #CRT
                  crt +
                  CRT_test,
                data = conspiracies)

summ(multi_lab, vifs = TRUE)
```

```{r}
AIC(se_polpsych_lab_2)
AIC(multi_lab)
```


## DV Chinese lab belief - interactions

```{r}
int_lab <- lm(conspiracy1_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 +
                  W2_INFO_9 +
                  
                  #political-psychology variables
                  #SDO +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  
                  #covid-anxiety
                  threat +
                  
                  #CRT
                  #crt +
                  CRT_test +
                
                  #interactions
                  (crt*RWA) +
                  (crt*SDO),
                data = conspiracies)

summ(int_lab, vifs = TRUE)
```


```{r}
AIC(multi_lab)
AIC(int_lab) # no support for interactions
```


## DV Chinese lab conspiracy - full model incl. conspiracy ideation

Re-adding in LOC variables for comprehensiveness and transparency.  

```{r}
full_lab <- lm(conspiracy1_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  W2_Internal_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #CRT
                  crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy2_sc +
                  conspiracy3_sc,
                data = conspiracies)

summ(full_lab, vifs = TRUE)
par(mfrow = c(2,2))
plot(full_lab)
```


```{r}
AIC(multi_lab)
AIC(full_lab)
```


# Interaction model

```{r}
full_int_lab <- lm(conspiracy1_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  #SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  W2_Internal_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #CRT
                  #crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy2_sc +
                  conspiracy3_sc +
                    
                  # interaction
                  (SDO*crt),
                data = conspiracies)

summ(full_int_lab, vifs = TRUE)
par(mfrow = c(2,2))
plot(full_int_lab)
```


```{r}
AIC(full_lab)
AIC(full_int_lab) # no support for interaction effect
```


# Modelling for belief in 5G origin conspiracy

## Plots of DV, incl. inverse hyperbolic sine transformation

```{r}
ihs <- function(x, theta){  # IHS transformation
  asinh(theta * x)/theta
}

ihs_loglik <- function(theta,x){
  
  ihs <- function(x, theta){  # function to IHS transform
    asinh(theta * x)/theta
  }
  
  n <- length(x)
  xt <- ihs(x, theta)
  
  log_lik <- -n*log(sum((xt - mean(xt))^2))- sum(log(1+theta^2*x^2))
  return(log_lik)
}     


# alternative using shapiro-wik test
shapiro_test_pvalue <- function(theta, x){ 
  x <- ihs(x, theta) 
  shapiro.test(x)$p.value 
}
```

```{r}
best_theta <- optimize(shapiro_test_pvalue, 
                       lower = 0.00001, upper = 50,
                       x = conspiracies$W2_Conspiracy_Theory3, 
                       maximum = TRUE)$maximum
best_theta
```


```{r}
conspiracies %>% 
  ggplot(aes(x = W2_Conspiracy_Theory3)) +
  geom_histogram(colour = "darkgrey", fill = "lightblue")

conspiracies <- conspiracies %>% 
  mutate(w2_conspiracy3_ihs = ihs(W2_Conspiracy_Theory3, best_theta))

conspiracies %>% 
  ggplot(aes(x = w2_conspiracy3_ihs)) +
  geom_histogram(colour = "darkgrey", fill = "lightblue")
```


## DV 5G conspiracy - singular IV models

```{r}
sdo_5g <- lm(conspiracy3_sc ~ SDO,
              data = conspiracies)

summ(sdo_5g)
```


```{r}
rwa_5g <- lm(conspiracy3_sc ~ RWA,
              data = conspiracies)

summ(rwa_5g)
```

```{r}
mid_news_5g <- lm(conspiracy3_sc ~ mid_level_news,
              data = conspiracies)

summ(mid_news_5g)
```

```{r}
social_m_5g <- lm(conspiracy3_sc ~ W2_INFO_5,
              data = conspiracies)

summ(social_m_5g)
```

## DV 5G conspiracy - socio-economic variables

```{r}
se_5g <- lm(conspiracy3_sc ~ W2_Gender_binary +
               W1_Education_binary +
               W1_Income_2019 +
               age_sc,
              data = conspiracies)

summ(se_5g, vifs = TRUE)
```

## DV 5G conspiracy - socio-economic variables + political/media

As with modelling above, fis_con is included instead of soc_con and right to avoid multicollinearity problem.  

```{r}
se_pol_5g <- lm(conspiracy3_sc ~ 
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   fis_con +
                   nat +
                   distrust_science + #distrust of scientists
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news + 
                   W2_INFO_5 + #social media
                   W2_INFO_9,
                 data = conspiracies)

summ(se_pol_5g, vifs = TRUE)
```


```{r}
AIC(se_5g)
AIC(se_pol_5g)
```


## DV 5G conspiracy - socio-economic variables + political/media + pol-psych

```{r}
se_polpsych_5g <- lm(conspiracy3_sc ~
                        #socio-economic variables
                        W2_Gender_binary +
                        W1_Education_binary +
                        W1_Income_2019 +
                        age_sc +
                        
                        #political and media variables
                        fis_con +
                        nat +
                        distrust_science + #distrust of scientists
                        red_top_tabloid + 
                        mid_level_news + 
                        elite_news + 
                        W2_INFO_5 + #social media
                        W2_INFO_9 + #family and friends
                     
                        #political-psychology variables
                        SDO +
                        RWA +
                        W2_DAI_Total +
                        W2_IOU_Total +
                        W2_Paranoia_Total +
                        W2_Internal_Total +
                        W2_Chance_Total +
                        W2_PO_Total,
                     data = conspiracies)

summ(se_polpsych_5g, vifs = TRUE)
```


```{r}
AIC(se_pol_5g)
AIC(se_polpsych_5g)
```

## DV 5G conspiracy - socio-economic variables + political/media + pol-psych + covid-threat

Dropping locus of control variables, internal and chance.  

```{r}
multi_5g <- lm(conspiracy3_sc ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_PO_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  # crt
                  crt +
                  CRT_test,
                 data = conspiracies)

summ(multi_5g, vifs = TRUE)
```


```{r}
AIC(se_polpsych_5g)
AIC(multi_5g)
```


As with the Chinese lab belief, the locus of control variables (W2_Internal_Total and W2_Chance_Total) appear unrelated to the DV, and are omitted in subsequent models.  


## DV 5G conspiracy - multivariate and interaction model

```{r}
int_5g <- lm(conspiracy3_sc ~
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 +
                  W2_INFO_9 +
                  
                  #political-psychology variables
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_PO_Total +
                  
                  #covid-anxiety
                  threat +
               
                  #crt
                  #crt +
                  CRT_test +
                  
                  #interactions
                  (crt * SDO),
             data = conspiracies)

summ(int_5g, vifs = TRUE)
```


```{r}
AIC(multi_5g)
AIC(int_5g) # very weak support for interaction term at this point
```


## DV 5G conspiracy - socio-economic variables + political/media + pol-psych + covid-threat and CRT + conspiracies

Re-adding in LOC variables for comprehensiveness and transparency.  

```{r}
full_5g <- lm(conspiracy3_sc ~
                #socio-economic variables
                W2_Gender_binary +
                W1_Education_binary +
                W1_Income_2019 +
                age_sc +
                  
                #political and media variables
                fis_con +
                nat +
                distrust_science + #distrust of scientists
                red_top_tabloid + 
                mid_level_news + 
                elite_news + 
                W2_INFO_5 + #social media
                W2_INFO_9 + #family and friends
                  
                #political-psychology variables
                SDO +
                RWA +
                W2_DAI_Total +
                W2_IOU_Total +
                W2_Paranoia_Total +
                W2_PO_Total +
                W2_Chance_Total +
                W2_Internal_Total +
                
                #covid-anxiety
                threat +
                
                #crt
                crt +
                CRT_test +
                  
                #conspiracies
                W1_Conspiracy_Total +
                conspiracy1_sc +
                conspiracy2_sc,
              data = conspiracies)

summ(full_5g, vifs = TRUE)
par(mfrow = c(2,2))
plot(full_5g)
```


```{r}
AIC(multi_5g)
AIC(full_5g)
```


```{r}
full_int_5g <- lm(conspiracy3_sc ~
                #socio-economic variables
                W2_Gender_binary +
                W1_Education_binary +
                W1_Income_2019 +
                age_sc +
                  
                #political and media variables
                fis_con +
                nat +
                distrust_science + #distrust of scientists
                red_top_tabloid + 
                mid_level_news + 
                elite_news + 
                W2_INFO_5 + #social media
                W2_INFO_9 + #family and friends
                  
                #political-psychology variables
                #SDO +
                RWA +
                W2_DAI_Total +
                W2_IOU_Total +
                W2_Paranoia_Total +
                W2_PO_Total +
                W2_Internal_Total +
                W2_Chance_Total +
                  
                #covid-anxety
                threat +
                
                #crt
                #crt +
                CRT_test +
                    
                #conspiracies
                W1_Conspiracy_Total +
                conspiracy1_sc +
                conspiracy2_sc +
                
                # interactions
                (crt*SDO),
              data = conspiracies)

summ(full_int_5g, vifs = TRUE)
par(mfrow = c(2,2))
plot(full_int_5g)
```


```{r}
# comparing AIC with and without interaction
AIC(full_5g)
AIC(full_int_5g) # very weak support for interaction effect
```


## DV 5G IHS conspiracy - singular IV models

```{r}
sdo_5g_ihs <- lm(w2_conspiracy3_ihs ~ SDO,
              data = conspiracies)

summ(sdo_5g_ihs)
```


```{r}
rwa_5g_ihs <- lm(w2_conspiracy3_ihs ~ RWA,
              data = conspiracies)

summ(rwa_5g_ihs)
```

```{r}
mid_news_5g_ihs <- lm(w2_conspiracy3_ihs ~ mid_level_news,
              data = conspiracies)

summ(mid_news_5g_ihs)
```

```{r}
social_m_5g_ihs <- lm(w2_conspiracy3_ihs ~ W2_INFO_5,
              data = conspiracies)

summ(social_m_5g_ihs)
```

## DV 5G IHS conspiracy - socio-economic variables

```{r}
se_5g_ihs <- lm(w2_conspiracy3_ihs ~ W2_Gender_binary +
               W1_Education_binary +
               W1_Income_2019 +
               age_sc,
              data = conspiracies)

summ(se_5g_ihs, vifs = TRUE)
```

## DV 5G IHS conspiracy - socio-economic variables + political/media

As with modelling above, fis_con is included instead of soc_con and right to avoid multicollinearity problem.  

```{r}
se_pol_5g_ihs <- lm(w2_conspiracy3_ihs ~ 
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   fis_con +
                   nat +
                   distrust_science + #distrust of scientists
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news + 
                   W2_INFO_5 + #social media
                   W2_INFO_9,
                 data = conspiracies)

summ(se_pol_5g_ihs, vifs = TRUE)
```


```{r}
AIC(se_5g_ihs)
AIC(se_pol_5g_ihs)
```


## DV 5G IHS conspiracy - socio-economic variables + political/media + pol-psych

```{r}
se_polpsych_5g_ihs <- lm(w2_conspiracy3_ihs ~
                        #socio-economic variables
                        W2_Gender_binary +
                        W1_Education_binary +
                        W1_Income_2019 +
                        age_sc +
                        
                        #political and media variables
                        fis_con +
                        nat +
                        distrust_science + #distrust of scientists
                        red_top_tabloid + 
                        mid_level_news + 
                        elite_news + 
                        W2_INFO_5 + #social media
                        W2_INFO_9 + #family and friends
                     
                        #political-psychology variables
                        SDO +
                        RWA +
                        W2_DAI_Total +
                        W2_IOU_Total +
                        W2_Paranoia_Total +
                        W2_Internal_Total +
                        W2_Chance_Total +
                        W2_PO_Total,
                     data = conspiracies)

summ(se_polpsych_5g_ihs, vifs = TRUE)
```


```{r}
AIC(se_pol_5g_ihs)
AIC(se_polpsych_5g_ihs)
```


## DV 5G IHS conspiracy - socio-economic variables + political/media + pol-psych + covid-threat

```{r}
multi_5g_ihs <- lm(w2_conspiracy3_ihs ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_PO_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  # crt
                  crt +
                  CRT_test,
                 data = conspiracies)

summ(multi_5g_ihs, vifs = TRUE)
```


```{r}
AIC(se_polpsych_5g_ihs)
AIC(multi_5g_ihs)
```

As with the Chinese lab belief, the locus of control variables (W2_Internal_Total and W2_Chance_Total) appear unrelated to the DV, and are omitted in subsequent models.  


## DV 5G IHS conspiracy - multivariate and interaction model


```{r}
int_5g_ihs <- lm(w2_conspiracy3_ihs ~
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_9 +
                  
                  #political-psychology variables
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_PO_Total +
                   
                  #covid-anxiety
                  threat +
               
                  #crt
                  crt +
                  CRT_test +
                  
                  #interactions
                  (W2_INFO_5 * SDO),
             data = conspiracies)

summ(int_5g_ihs, vifs = TRUE)
```


```{r}
AIC(multi_5g_ihs)
AIC(int_5g_ihs) # very weak support for interaction term at this point
```


## DV 5G IHS conspiracy - socio-economic variables + political/media + pol-psych + covid-threat and CRT + conspiracies

Re-adding in LOC variables for comprehensiveness and transparency.  

```{r}
full_5g_ihs <- lm(w2_conspiracy3_ihs ~
                #socio-economic variables
                W2_Gender_binary +
                W1_Education_binary +
                W1_Income_2019 +
                age_sc +
                  
                #political and media variables
                fis_con +
                nat +
                distrust_science + #distrust of scientists
                red_top_tabloid + 
                mid_level_news + 
                elite_news + 
                W2_INFO_5 + #social media
                W2_INFO_9 + #family and friends
                  
                #political-psychology variables
                SDO +
                RWA +
                W2_DAI_Total +
                W2_IOU_Total +
                W2_Paranoia_Total +
                W2_PO_Total +
                W2_Internal_Total +
                W2_Chance_Total +
                
                #covid-anxiety
                threat +
                
                #crt
                crt +
                CRT_test +
                  
                #conspiracies
                W1_Conspiracy_Total +
                conspiracy1_sc +
                conspiracy2_sc,
              data = conspiracies)

summ(full_5g_ihs, vifs = TRUE)
par(mfrow = c(2,2))
plot(full_5g_ihs)
```

```{r}
AIC(multi_5g_ihs)
AIC(full_5g_ihs)
```


```{r}
full_int_5g_ihs <- lm(w2_conspiracy3_ihs ~
                #socio-economic variables
                W2_Gender_binary +
                W1_Education_binary +
                W1_Income_2019 +
                age_sc +
                  
                #political and media variables
                fis_con +
                nat +
                distrust_science + #distrust of scientists
                red_top_tabloid + 
                mid_level_news + 
                elite_news + 
                W2_INFO_5 + #social media
                W2_INFO_9 + #family and friends
                  
                #political-psychology variables
                #SDO +
                RWA +
                W2_DAI_Total +
                W2_IOU_Total +
                W2_Paranoia_Total +
                W2_PO_Total +
                W2_Chance_Total +
                W2_Internal_Total +
                
                #covid-anxety
                threat +
                
                #crt
                #crt +
                CRT_test +
                    
                #conspiracies
                W1_Conspiracy_Total +
                conspiracy1_sc +
                conspiracy2_sc +
                
                # interactions
                (crt*SDO),
              data = conspiracies)

summ(full_int_5g_ihs, vifs = TRUE)
```


```{r}
# comparing AIC with and without interaction
AIC(full_5g_ihs)
AIC(full_int_5g_ihs) # no support for interaction effect
```


## DV 5G conspiracy poisson regression model

```{r}
conspiracies %>% 
  mutate(
    sdo_deciles = cut_number(SDO,10)
  ) %>%
  group_by(sdo_deciles) %>% 
  summarise(
    mean_5g = mean(W2_Conspiracy_Theory3),
    var_5g = sd(W2_Conspiracy_Theory3) ^ 2
  )

conspiracies %>% 
  mutate(
    social_media = cut_interval(W2_INFO_5,5)
  ) %>%
  group_by(social_media) %>% 
  summarise(
    mean_5g = mean(W2_Conspiracy_Theory3),
    var_5g = sd(W2_Conspiracy_Theory3) ^ 2
  )
```


The tables above suggest overdispersion of the data.  As a result, running quasipoisson models, as suggested by [Building Your Statistical Horizons](https://bookdown.org/roback/bookdown-bysh/ch-poissonreg.html).    

```{r}
full_5g_poiss <- glm(W2_Conspiracy_Theory3 ~
                           #socio-economic variables
                           W2_Gender_binary +
                           W1_Education_binary +
                           W1_Income_2019 +
                           age_sc +
                           
                           #political and media variables
                           fis_con +
                           nat +
                           distrust_science + #distrust of scientists
                           red_top_tabloid + 
                           mid_level_news + 
                           elite_news + 
                           W2_INFO_5 + #social media
                           W2_INFO_9 + #family and friends
                           
                           #political-psychology variables
                           SDO +
                           RWA +
                           W2_DAI_Total +
                           W2_IOU_Total +
                           W2_Paranoia_Total +
                           W2_PO_Total +
                           W2_Internal_Total +
                           W2_Chance_Total +
                           
                           #covid-anxiety
                           threat +
                           
                           #crt
                           crt +
                           CRT_test +
                           
                           #conspiracies
                           W1_Conspiracy_Total +
                           conspiracy1_sc +
                           conspiracy2_sc,
                         family = "quasipoisson", data = conspiracies)

summary(full_5g_poiss)
```

```{r}
# plotting coefficients for poisson model
cons <- as_tibble(
  exp(confint(full_5g_poiss))
)

names(cons) <- c("lower","upper")

cons$estimate <- exp(coef(full_5g_poiss))
cons$variable <- names(coef(full_5g_poiss))

cons %>% 
  filter(variable != "(Intercept)") %>%
  gather(
    level,ci,lower:upper
  ) %>% 
  ggplot(aes(x = fct_reorder(variable,estimate), y = estimate)) +
  geom_hline(yintercept = 1, linetype = "dashed", size = 1, 
             colour = "darkgrey") +
  geom_point() +
  geom_line(aes(x = fct_reorder(variable,estimate), y = ci)) +
  coord_flip() +
  theme_classic()
```

## DV 5G belief - poisson regression, interaction term

```{r}
## interaction term added
full_int_5g_poiss <- glm(W2_Conspiracy_Theory3 ~
                           #socio-economic variables
                           W2_Gender_binary +
                           W1_Education_binary +
                           W1_Income_2019 +
                           age_sc +
                           
                           #political and media variables
                           fis_con +
                           nat +
                           distrust_science + #distrust of scientists
                           red_top_tabloid + 
                           mid_level_news + 
                           elite_news + 
                           W2_INFO_5 + #social media
                           W2_INFO_9 + #family and friends
                           
                           #political-psychology variables
                           #SDO +
                           RWA +
                           W2_DAI_Total +
                           W2_IOU_Total +
                           W2_Paranoia_Total +
                           W2_PO_Total +
                           W2_Internal_Total +
                           W2_Chance_Total +
                           
                           #covid-anxiety
                           threat +
                           
                           #crt
                           #crt +
                           CRT_test +
                           
                           #conspiracies
                           W1_Conspiracy_Total +
                           conspiracy1_sc +
                           conspiracy2_sc +
                           
                           # interactions
                           (crt*SDO),
                         family = "quasipoisson", data = conspiracies)

summary(full_int_5g_poiss)
```


```{r}
# plotting poiss coefficients (not incl. interaction due to scale size)
cons <- as_tibble(
  exp(confint(full_int_5g_poiss))
)

names(cons) <- c("lower","upper")

cons$estimate <- exp(coef(full_int_5g_poiss))
cons$variable <- names(coef(full_int_5g_poiss))

cons %>% 
  filter(variable != "(Intercept)" & variable != "crt:SDO") %>%
  gather(
    level,ci,lower:upper
  ) %>% 
  ggplot(aes(x = fct_reorder(variable,estimate), y = estimate)) +
  geom_hline(yintercept = 1, linetype = "dashed", size = 1, 
             colour = "darkgrey") +
  geom_point() +
  geom_line(aes(x = fct_reorder(variable,estimate), y = ci)) +
  coord_flip() +
  theme_classic()
```


```{r}
# drop in deviance test
phi <- sum(resid(full_int_5g_poiss, type='pearson')^2) / full_int_5g_poiss$df.residual
drop_in_dev <- full_5g_poiss$deviance - full_int_5g_poiss$deviance
diff_in_df <- full_5g_poiss$df.residual - full_int_5g_poiss$df.residual
f_stat <- drop_in_dev / summary(full_int_5g_poiss)$dispersion
f_stat

1-pf(f_stat, diff_in_df, full_int_5g_poiss$df.residual)
```


## Random forest for 5G belief

```{r}
pacman::p_load(randomForest)

conspiracies2 <- model.matrix(full_5g_ihs)[,-1] %>% as.data.frame()
y <- model.matrix(full_lab) %>% as.data.frame %>%
  dplyr::select(conspiracy3_sc) %>% as_vector() %>% 
  ihs(theta = best_theta)

set.seed(123)
rf_mod_5g <- randomForest(y ~ .,
                          data = conspiracies2, ntree = 750,
                          mtry = 8, importance = TRUE)

varImpPlot(rf_mod_5g)
```


# Modelling for belief in Chinese meat market origin

## DV Chinese meat market - singular IV models

```{r}
sdo_meat <- lm(conspiracy2_sc ~ SDO,
              data = conspiracies)

summ(sdo_meat)
```

```{r}
rwa_meat <- lm(conspiracy2_sc ~ RWA,
              data = conspiracies)

summ(rwa_meat)
```

```{r}
mid_news_meat <- lm(conspiracy2_sc ~ mid_level_news,
              data = conspiracies)

summ(mid_news_meat)
```

```{r}
social_m_meat <- lm(conspiracy2_sc ~ W2_INFO_5,
              data = conspiracies)

summ(social_m_meat)
```

## DV Chinese meat market belief - socio-economic variables

```{r}
se_meat <- lm(conspiracy2_sc ~ W2_Gender_binary +
               W1_Education_binary +
               W1_Income_2019 +
               age_sc,
              data = conspiracies)

summ(se_meat, vifs = TRUE)
```

## DV Chinese meat market belief - socio-economic variables + political/media

```{r}
se_pol_meat <- lm(conspiracy2_sc ~ 
                   
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   right +
                   soc_con +
                   fis_con +
                   nat +
                   distrust_science + #distrust of scientists
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news + 
                   W2_INFO_5 + #social media
                   W2_INFO_9, #family and friends
                 data = conspiracies)

summ(se_pol_meat, vifs = TRUE)
```

```{r}
AIC(se_meat)
AIC(se_pol_meat)
```


## DV Chinese meat market belief - socio-economic variables + political/media + pol-psych

```{r}
se_polpsych_meat <- lm(conspiracy2_sc ~
                        
                        #socio-economic variables
                        W2_Gender_binary +
                        W1_Education_binary +
                        W1_Income_2019 +
                        age_sc +
                        
                        #political and media variables
                        fis_con +
                        nat +
                        distrust_science + #distrust of scientists
                        red_top_tabloid + 
                        mid_level_news + 
                        elite_news + 
                        W2_INFO_5 + #social media
                        W2_INFO_9 + #family and friends
                     
                        #political-psychology variables
                        SDO +
                        RWA +
                        W2_DAI_Total +
                        W2_IOU_Total +
                        W2_Paranoia_Total +
                        W2_Internal_Total +
                        W2_Chance_Total +
                        W2_PO_Total,
                      data = conspiracies)

summ(se_polpsych_meat, vifs = TRUE)
```


```{r}
AIC(se_pol_meat)
AIC(se_polpsych_meat)
```


## DV Chinese meat market belief - socio-economic variables + political/media + pol-psych + covid-threat + CRT

```{r}
multi_meat <- lm(conspiracy2_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  W2_Internal_Total +
                  W2_Chance_Total +
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Internal_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  
                  #covid-anxiety
                  threat +
                  
                  #CRT
                  crt +
                  CRT_test,
                data = conspiracies)

summ(multi_meat, vifs = TRUE)
```

```{r}
AIC(se_polpsych_meat)
AIC(multi_meat)
```



## DV Chinese meat market belief - full model incl. conspiracy ideation

Re-adding in LOC variables for comprehensiveness and transparency.  

```{r}
full_meat <- lm(conspiracy2_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Internal_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  
                  #covid-anxety
                  threat +
                 
                  #CRT
                  crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy1_sc +
                  conspiracy3_sc,
                data = conspiracies)

summ(full_meat, vifs = TRUE)
```

```{r}
full_int_meat <- lm(conspiracy2_sc ~
                  
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news + 
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  #SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Internal_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  
                  #covid-anxety
                  threat +
                 
                  #CRT
                  #crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy1_sc +
                  conspiracy3_sc +
                  
                  #interaction
                  (SDO*crt),
                data = conspiracies)

summ(full_int_meat, vifs = TRUE)
```

```{r}
AIC(multi_meat)
AIC(full_meat)
AIC(full_int_meat) # very weak support for interactions
```


# Summary of final models

```{r}
# Chinese lab belief - full set of variables
to_plot <- c("age_sc","W1_Education_binary1","W2_Gender_binary2",
             "W1_Income_2019","elite_news","W2_INFO_9","mid_level_news",
             "W2_INFO_5","red_top_tabloid","threat","W2_DAI_Total",
             "distrust_science","fis_con","W2_IOU_Total","W2_Chance_Total",
             "W2_Internal_Total","W2_PO_Total","nat","W2_Paranoia_Total",
             "RWA","SDO","crt","CRT_test","W1_Conspiracy_Total")
names(to_plot) <- c("Age","Education","Gender","Income","Elite news",
              "Family and friends","Mid-level news","Social media",
              "Tabloid news","COVID-19 anxiety","Death anxiety",
              "Distrust scientists","Fiscal conservatism",
              "Intolerance of uncertainty","LOC: chance","LOC: internal",
              "LOC: powerful others","Nationalism","Paranoia","RWA",
              "SDO","CRT","CRT pre-exposure","Conspiracy ideation")

lab_vars1 <- c(to_plot, "conspiracy3_sc","conspiracy2_sc")
names(lab_vars1) <- c(names(to_plot), "5G belief", "Meat market belief")
lab_vars1 <- lab_vars1[sort(names(lab_vars1))]
lab_vars <- c(lab_vars1[-1],"conspiracy3_sc")
names(lab_vars) <- c(names(lab_vars1)[-1],"5G belief")


plot_coefs(
  full_lab,
  coefs = lab_vars) +
  theme(legend.position = "top") +
  labs(
    x = "Estimate: Belief in Wuhan laboratory origin"
  )

summary(full_lab)$r.squared
summary(full_lab)$adj.r.squared
```

```{r}
# 5G belief - full set of variables, raw data is DV
fiveg_vars <- c(to_plot, "conspiracy2_sc","conspiracy1_sc")
names(fiveg_vars) <- c(names(to_plot),"Meat market belief",
                     "Wuhan lab belief")
fiveg_vars <- fiveg_vars[sort(names(fiveg_vars))]

plot_coefs(
  full_5g,
  coefs = fiveg_vars) +
  labs(
    x = "Estimate: Belief in 5G origin"
  )

summary(full_5g)$r.squared
summary(full_5g)$adj.r.squared

```

```{r}
# plot for IHS model
plot_coefs(
  full_5g_ihs,
  coefs = fiveg_vars) +
  labs(
    x = "Estimate: Belief in 5G origin (IHS transformation)"
  ) 
```



```{r}
# 5G belief - full set of variables and poisson
summ(full_5g_poiss)
plot_coefs(
  full_5g_poiss,
  coefs = fiveg_vars
  ) +
  labs(
    x = "Estimate: Belief in 5G origin (poisson)"
  )
```


```{r}
# Chinese meat market model - full set of variables
meat_vars1 <- c(to_plot, "conspiracy3_sc","conspiracy1_sc")
names(meat_vars1) <- c(names(to_plot),"5G belief",
                     "Wuhan lab belief")
meat_vars1 <- meat_vars1[sort(names(meat_vars1))]
meat_vars <- c(meat_vars1[-1],"conspiracy3_sc")
names(meat_vars) <- c(names(meat_vars1)[-1],"5G belief")

plot_coefs(
  full_meat,
  coefs = meat_vars) +
  labs(
    x = "Estimate: Belief in meat market origin"
  )
summary(full_meat)$r.squared
summary(full_meat)$adj.r.squared
```

## Combined plot of models

```{r, message = FALSE, warning = FALSE}
model_vars <- c("W1_Education_binary1","crt",
                "red_top_tabloid","mid_level_news",
                "W2_INFO_5","W2_INFO_9","SDO",
                "RWA")
names(model_vars) <- c("Post-secondary education","CRT",
                       "Tabloid news","Mid-level news",
                       "Social media",
                       "Family and friends",
                       "SDO","RWA")

model_vars <- model_vars[sort(names(model_vars))]

plot_coefs(
  full_lab,full_5g,full_meat,
  model.names = c("Wuhan lab","5G","Meat market"),
  coefs = model_vars) +
  labs(
    x = "Estimate: OLS model comparison"
  ) + 
  theme(#axis.title.x = element_text(hjust = 0.33),
        legend.title = element_text(size = 9),
        legend.position = c(1,1), legend.direction = "vertical",
        legend.justification = c(1,1),
        legend.background = element_rect(colour = "darkgrey", 
                                         fill = "white"))
```


## Conspiracies and social distancing

```{r}
# loading package for multi nom
pacman::p_load(nnet)
```


```{r}
## making a dataset of variables included in the models above
## plus DV's for social distancing and vaccination

vars <- model.matrix(full_lab)[,-1] %>% as.data.frame() %>% names()
vars <- c(vars,"w2_conspiracy3_ihs","W2_Internal_Total",
          "W2_Chance_Total","W2_Conspiracy_Theory1",
          "W2_Conspiracy_Theory2","W2_Conspiracy_Theory3",
          "W2_Conspiracy_Theory4","W2_Conspiracy_Theory5",
          "conspiracy4_sc","conspiracy5_sc","conspiracy1_sc",
          "W2_PO_Total","pid")
vars[1] <- str_sub(vars[1],1,str_length(vars[1])-1)
vars[2] <- str_sub(vars[2],1,str_length(vars[2])-1)

conspiracies2 <- conspiracies %>% 
  dplyr::select(one_of(vars)) %>% 
  na.omit()

conspiracies2 <- merge(
  conspiracies2,
  conspiracies %>% dplyr::select(pid,W2_SocialDistance10,
                                 W2_SocialDistance11,
                                 W2_SocialDistance12,
                                 W2_SocialDistance14,
                                 W2_C19_Vax_Self,
                                 W2_C19_Vax_Child, W2_Trust_Body1,
                                 W2_Trust_Body2,W2_Trust_Body5),
  by = "pid", all.x = TRUE
)

```


```{r}
# functions to inspact multinomial logit model
z_score <- function(model){
  z <- summary(model)$coefficients/summary(model)$standard.errors
  return(z)
}

p_value <- function(model){
  z <- z_score(model)
  p <- (1 - pnorm(abs(z), 0, 1)) * 2
  return(p)
}
```


```{r}
# social distance scale
sd_keys <- list(sd = cs(W2_SocialDistance10,
                        W2_SocialDistance11,
                        W2_SocialDistance12,
                        W2_SocialDistance14))

sd_test <- scoreItems(sd_keys, conspiracies2, min = 1, max = 5)
head(sd_test$scores)
summary(sd_test$alpha)  # Scale alpha
conspiracies2$social_distance <- rescale01(sd_test$scores, na.rm = TRUE)
conspiracies2$social_distance <- c(conspiracies2$social_distance)  # Ensure variable is numeric and not matrix class

describe(conspiracies2$social_distance)
ggplot(conspiracies2, aes(x = social_distance, y = ..density..)) +
  geom_histogram(binwidth = 0.1, colour = "black", fill = "lightblue")
```


```{r}
dist_full <- lm(social_distance ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  W2_Internal_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #CRT
                  crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy1_sc +
                  conspiracy2_sc +
                  conspiracy3_sc,
                data = conspiracies2)

dist_plots1 <- c("age_sc","W2_Gender_binary2","W2_INFO_9",
                "threat","W2_DAI_Total","distrust_science",
                "W2_IOU_Total","W2_Internal_Total","RWA","SDO",
                "W1_Conspiracy_Total","conspiracy3_sc",
                "conspiracy2_sc","conspiracy1_sc")
names(dist_plots1) <- c("Age","Gender",
              "Family and friends","COVID-19 anxiety","Death anxiety",
              "Distrust scientists","Intolerance of uncertainty",
              "LOC: internal","RWA",
              "SDO","Conspiracy ideation","5G belief",
              "Meat market belief","Wuhan lab belief")

dist_plots1 <- dist_plots1[sort(names(dist_plots1))]
dist_plots <- c(dist_plots1[-1],"conspiracy3_sc")
names(dist_plots) <- c(names(dist_plots1)[-1],"5G belief")


summ(dist_full, vifs = TRUE)
plot_coefs(dist_full,
           coefs = dist_plots
           ) +
  labs(
    x = "Estimate: social distancing motivation"
  )
par(mfrow = c(2,2))
plot(dist_full)
```


## Multinomial model for vaccine acceptance

```{r}
count(conspiracies2,sum()) %>%  mutate(`%` = n / sum(n))

vax_full <- multinom(W2_C19_Vax_Self ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  fis_con +
                  nat +
                  distrust_science + #distrust of scientists
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_DAI_Total +
                  W2_IOU_Total +
                  W2_Paranoia_Total +
                  W2_Chance_Total +
                  W2_PO_Total +
                  W2_Internal_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #CRT
                  crt +
                  CRT_test +
                  
                  #conspiracies
                  W1_Conspiracy_Total +
                  conspiracy1_sc +
                  conspiracy2_sc +
                  conspiracy3_sc,
                data = conspiracies2)
```


```{r}
vax_plots1 <- c("age_sc","W2_Gender_binary2","W1_Income_2019","threat",
               "distrust_science","nat","RWA","SDO","W1_Conspiracy_Total",
               "conspiracy3_sc","conspiracy2_sc","conspiracy1_sc")

names(vax_plots1) <- c("Age","Gender","Income","COVID-19 anxiety",
                      "Distrust scientists","Nationalism",
                      "RWA","SDO","Conspiracy ideation",
                      "5G belief","Meat market belief","Wuhan lab belief")

vax_plots1 <- vax_plots1[sort(names(vax_plots1))]
vax_plots <- c(vax_plots1[-1],"conspiracy3_sc")
names(vax_plots) <- c(names(vax_plots1[-1]),"5G belief")

tidies <- tidy(vax_full) %>%
  filter(term %in% vax_plots) %>% 
  mutate(
    odds_ratio = exp(estimate),
    conf.low = estimate - std.error * qnorm(0.975),
    conf.high = estimate + std.error * qnorm(0.975),
    conf.low.exp = exp(estimate - std.error * qnorm(0.975)),
    conf.high.exp = exp(estimate + std.error * qnorm(0.975)),
    y.level = fct_recode(as.factor(y.level),
                              "No" = "2",
                              "Maybe" = "3"),
    term = fct_rev(fct_drop(fct_relevel(term, vax_plots)))) %>%
  rename(Level = y.level)  

ggplot(data = tidies, 
       aes(y = term, 
           x = estimate, xmin = conf.low,
                          xmax = conf.high, colour = Level)) + 
  geom_vline(xintercept = 0, linetype = 2, size = .25) +
  ggstance::geom_linerangeh(
  aes(y = term, xmin = conf.low,
      xmax = conf.high, colour = Level),
  position = ggstance::position_dodgev(height = 0.62), size = 0.8) +
  geom_point(
    aes(y = term, 
        x = estimate, colour = Level, shape = Level),
    position = ggstance::position_dodgev(height = 0.62),
    fill = "white", size = 3, stroke = 1, show.legend = TRUE) +
  scale_colour_manual(values = get_colors("CUD Bright",num.colors = 2)) +
  theme_nice(legend.pos = "right") +
  scale_shape_manual(values = c(21,22)) +
  scale_y_discrete(labels = rev(names(vax_plots))) +
  drop_y_gridlines() +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size = 10),
        panel.grid.major.x = element_line(linetype = "solid")) +
  labs(
    x = "Estimate: Vaccine acceptance"
  ) + 
  theme(legend.title = element_text(size = 9),
        legend.position = c(1,1), legend.direction = "vertical",
        legend.justification = c(1,1),
        legend.background = element_rect(colour = "darkgrey", 
                                         fill = "white"))
```

## Table summarising variables

```{r}
all_vars <- model.matrix(dist_full)[,-1] %>% as_tibble()
var_summaries <- tibble(
  variable = names(all_vars),
  mean = all_vars %>% map_dbl(mean, na.rm = TRUE),
  sd = all_vars %>% map_dbl(sd, na.rm = TRUE)
)

#write.csv(var_summaries,"variable_summaries.csv")
```


```{r}
conspiracies2 %>% 
  count(
    to_factor(W2_C19_Vax_Self)
  )
```

