---
title: "covid_conspiracies_markdown4"
author: "Michael Marshall"
date: "14/03/2021"
output: github_document
---

## Loading Packages and Data

```{r, message = FALSE, warnings = FALSE}
pacman::p_load(tidyverse, stringr, ggridges, forcats, labelled, leaps,
               psych, corrr, cowplot, expss, haven, interplot,
               interactions, jtools,labelled, pscl, psych, 
               sjPlot, skimr)

load("COVID W1_W2_W3 Cleaned 2878.RData") # needs to be in your wd
```

## Rescaling variable

```{r}
## [rescale01] Function to rescale a variable from 0 to 1
rescale01 <- function(x, ...) {
  (x - min(x, ...)) / ((max(x, ...)) - min(x, ...))
}
```

## Summary and distribution of different COVID specific conspiracies

```{r, message = FALSE, warning = FALSE}
# plotting density of different covid conspiracies
df %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  gather(conspiracy_code, belief,
         W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>%
  mutate(conspiracy_code = as.factor(conspiracy_code)) %>%
  filter(!conspiracy_code %in% c("W2_Conspiracy_Theory4",
                                 "W2_Conspiracy_Theory5")) %>% 
  ggplot(aes(x = belief, y = conspiracy_code, height = ..density..)) +
  geom_density_ridges(aes(rel_min_height = 0.005),
                      stat = "density",
                      fill = get_colors("CUD Bright",num.colors = 1)) +
  theme_nice() +
  scale_y_discrete(labels = c("Wuhan laboratory","Meat market","5G")) +
  labs(y = NULL, x = "Belief scale (0-100)",
       caption = "Distribution of origin theory belief") +
  theme(plot.caption = element_text(hjust = 0.61,
                                    face = "bold",
                                    size = 10),
        axis.title.x = element_text(size = 8,
                                    hjust = 0.5)
  )
```

```{r}
#pacman::p_load(patchwork)
df %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  gather(conspiracy_code, belief,
         W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>%
  mutate(conspiracy_code = fct_recode(
    as.factor(conspiracy_code),
    "Wuhan laboratory" = "W2_Conspiracy_Theory1",
    "Meat market" = "W2_Conspiracy_Theory2",
    "5G" = "W2_Conspiracy_Theory3",
    "4" = "W2_Conspiracy_Theory4",
    "5" = "W2_Conspiracy_Theory5")
    ) %>%
  filter(!conspiracy_code %in% c("4","5")) %>% 
  mutate(
    order_var = ifelse(conspiracy_code == "Meat market", 1,
                       ifelse(conspiracy_code == "Wuhan laboratory",2,3))
  ) %>% 
  ggplot(aes(x = belief)) +
  geom_density(fill = get_colors("CUD Bright",num.colors = 1),
               alpha = 0.8) +
  theme_nice() +
  facet_wrap(~fct_reorder(conspiracy_code,order_var), 
             scales = "free_y", ncol = 1) +
  labs(y = "Density", 
       x = "Distribution of origin theory belief")
```


## Cleaning dataset

The following code filters down to just those observations that have completed the battery of questions relating to COVID specific conspiracies.  It also creates a tibble counting the missing observations, which can be useful to have as an object.  

```{r}
# filtering for completed dependent variable
conspiracies <- df %>% 
  filter(!is.na(W2_Conspiracy_Theory1) |
           !is.na(W2_Conspiracy_Theory2) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory4) |
           !is.na(W2_Conspiracy_Theory5)) %>% 
  rename(W1_Housing_tenure = W1_Hosuing_tenure)

# function to count NAs
count_na <- function(x){
  sum(is.na(x))
}

conspiracies %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  map_int(count_na)

missing <- tibble(
  variable = names(conspiracies),
  NAs = conspiracies %>% map_int(count_na)
)

#View(missing)
```

Due to some measurement error in original *W1_Education_binary* variable, the code below overwrites the variable, and creates a dummy for degree educated respondents (undergrad OR postgrad = 1).  

```{r}
conspiracies <- conspiracies %>% 
  mutate(
    W1_Education_binary = ifelse(
      W1_Education %in% c(5,7), 1, 0
    )
  )
count(conspiracies, W1_Education, W1_Education_binary)
```


The code below turns the *preferred newspaper* variables into dummy variables, as they were previously coded as *1=Yes* and everything else as *NA*.  

```{r}

# making preferred newspaper dummy variable (i.e. replacing NA with 0)
na_to_zero <- function(x){
  x[is.na(x)] <- 0
  x <- as.numeric(x)
  return(x)
} 

paper_vars <- rep(str_c("W2_Newspaper_prefer",seq(1,11,1)))

conspiracies[paper_vars] <- conspiracies[paper_vars] %>% 
  map_df(na_to_zero)

conspiracies <- conspiracies %>% 
  mutate(
    red_top_tabloid = ifelse(
      W2_Newspaper_prefer3 == 1 | W2_Newspaper_prefer2 == 1 |
        W2_Newspaper_prefer7 == 1 | W2_Newspaper_prefer8 == 1 |
        W2_Newspaper_prefer9 == 1, 1, 0),
    mid_level_news = ifelse(
      W2_Newspaper_prefer1 == 1 | W2_Newspaper_prefer4 == 1, 1, 0),
    elite_news = ifelse(
      W2_Newspaper_prefer5 == 1 | W2_Newspaper_prefer6 == 1 |
        W2_Newspaper_prefer10 == 1 | 
        W2_Newspaper_prefer11 == 1, 1, 0)
  )

conspiracies %>% 
  count(red_top_tabloid, mid_level_news, elite_news)
```

```{r}
# Creating DVs
# [ethno] ethnocentrism
eth_keys <- list(ethno = cs(W2_Nationalism1,W2_Nationalism2))
eth_test <- scoreItems(eth_keys, conspiracies, min = 1, max = 5)
head(eth_test$scores)
eth_test$alpha  # Scale alpha
conspiracies$ethno <- rescale01(eth_test$scores, na.rm = TRUE)
conspiracies$ethno <- c(conspiracies$ethno)  # Ensure variable is numeric and not matrix class
describe(conspiracies$ethno)
```

```{r}
# Right wing authoritarianism
rwa_keys <- list(rwa = cs(W1_Authoritarianism1_R,
                          W1_Authoritarianism2,
                          W1_Authoritarianism3,
                          W1_Authoritarianism4_R, 
                          W1_Authoritarianism5_R,
                          W1_Authoritarianism6))

rwa_test <- scoreItems(rwa_keys, conspiracies, min = 1, max = 5)
head(rwa_test$scores)
summary(rwa_test$alpha)  # Scale alpha
conspiracies$RWA <- rescale01(rwa_test$scores, na.rm = TRUE)
conspiracies$RWA <- c(conspiracies$RWA)  # Ensure variable is numeric and not matrix class

describe(conspiracies$RWA)
```

```{r}
## [SDO] Social Dominance Orientation
sdo_keys <- list(sdo = cs(W1_Social_Dominance1,
                          W1_Social_Dominance2_R,
                          W1_Social_Dominance3_R,
                          W1_Social_Dominance4,
                          W1_Social_Dominance5_R,
                          W1_Social_Dominance6, 
                          W1_Social_Dominance7,
                          W1_Social_Dominance8_R))
sdo_test <- scoreItems(sdo_keys, conspiracies, min = 1, max = 5)
head(sdo_test$scores)
summary(sdo_test$alpha)  # Scale alpha
conspiracies$SDO <- rescale01(sdo_test$scores, na.rm = TRUE)
conspiracies$SDO <- c(conspiracies$SDO)  # Ensure variable is numeric and not matrix class

summary(conspiracies$SDO)
```

```{r}
## [threat] Covid-19 related Threat
summary(conspiracies$W2_COVID19_anxiety)
conspiracies$threat <- rescale01(conspiracies$W2_COVID19_anxiety)
conspiracies %>% 
  dplyr::select(W2_COVID19_anxiety, threat) %>%
  correlate()
```

```{r}
## [right] Right-Wing political views
table(conspiracies$W1_Political_Scale)
conspiracies$right <- rescale01(conspiracies$W1_Political_Scale)
conspiracies %>% 
  dplyr::select(W1_Political_Scale, right) %>%
  correlate()
```

```{r}
## [soc.con] Social conservatism
table(conspiracies$W1_Political_Abortion_SSM)
conspiracies$soc_con <- rescale01(
  conspiracies$W1_Political_Abortion_SSM)
conspiracies %>% 
  dplyr::select(W1_Political_Abortion_SSM, soc_con) %>%
  correlate()
```

```{r}
## [fis.con] Fiscal conservatism
table(conspiracies$W1_Political_Fiscal)
conspiracies$fis_con <- rescale01(conspiracies$W1_Political_Fiscal)
conspiracies %>% 
  dplyr::select(W1_Political_Fiscal, fis_con) %>%
  correlate()
```

```{r}
## [age.c] Age (in years)
summary(conspiracies$W2_Age_year)
conspiracies$age_sc <- rescale01(conspiracies$W2_Age_year)
```

```{r}
# conspiracy ideation
consp_keys <- list(consp = cs(W1_Conspiracy_1,
                          W1_Conspiracy_2,
                          W1_Conspiracy_3,
                          W1_Conspiracy_4,
                          W1_Conspiracy_5))
consp_test <- scoreItems(consp_keys, conspiracies, min = 1, max = 11)
head(consp_test$scores)
consp_test$alpha  # Scale alpha

cor(consp_test$scores, conspiracies$W1_Conspiracy_Total)

mean(
  round(rescale01(consp_test$scores, na.rm = T), 4) ==
    round(rescale01(conspiracies$W1_Conspiracy_Total, na.rm = T), 4)
) # scale is equal to pre-existing variable in dataset
```

```{r}
# intolerance of uncertainty
iou_keys <- list(iou = cs(W2_IOU1, W2_IOU2,W2_IOU3, W2_IOU4,
                          W2_IOU5, W2_IOU5,W2_IOU6,W2_IOU7,
                          W2_IOU7,W2_IOU8,W2_IOU9,W2_IOU10,
                          W2_IOU11,W2_IOU12))
iou_test <- scoreItems(iou_keys, conspiracies, min = 1, max = 5)
head(iou_test$scores)
iou_test$alpha  # Scale alpha

cor(iou_test$scores, conspiracies$W2_IOU_Total)

mean(
  round(rescale01(iou_test$scores, na.rm = T), 4) ==
    round(rescale01(conspiracies$W2_IOU_Total, na.rm = T), 4)
) # scale is equal to pre-existing variable in dataset
```


```{r}
factors <- c("W1_Ethnicity",
             "W2_Gender_binary")
```

```{r}
# turning to factors
conspiracies[factors] <- conspiracies[factors] %>% 
  map_df(as.factor)
```

```{r}
# renaming trust in science
conspiracies <- conspiracies %>% 
  rename(distrust_science = W2_Trust_Body6)
```


```{r}
# rescaling the remaing numeric variables
numerics <- c("W1_Conspiracy_Total","W2_IOU_Total", "W2_INFO_5",
              "W2_INFO_9","distrust_science","W1_Income_2019")

conspiracies[numerics] <- conspiracies[numerics] %>% 
  map_df(rescale01, na.rm = TRUE)
```


```{r}
# creating scaled versions of each conspiracy belief
conspiracies$conspiracy1_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory1, na.rm = TRUE
)

conspiracies$conspiracy2_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory2, na.rm = TRUE
)

conspiracies$conspiracy3_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory3, na.rm = TRUE
)

conspiracies$conspiracy4_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory4, na.rm = TRUE
)

conspiracies$conspiracy5_sc <- rescale01(
  conspiracies$W2_Conspiracy_Theory5, na.rm = TRUE
)
```


## Distribution of variables

A for loop to look at distribution of potential independent variables (numeric only).  

```{r}
plot_vars <- conspiracies %>% 
  dplyr::select(
    one_of(numerics),ethno,RWA,SDO,threat,right,soc_con,fis_con
    ) %>%
  names()

for(i in seq_along(plot_vars)){
  
  x1 <- conspiracies[plot_vars][i] %>% as_vector()
  
  print(
    ggplot(data = NULL, aes(x = x1)) +
      geom_vline(aes(xintercept = mean(x1, na.rm =TRUE)), 
                 colour = "black",
                 linetype = "dashed") +
      geom_vline(aes(xintercept = median(x1, na.rm =TRUE)), 
                 colour = "red",
                 linetype = "dashed") +
      geom_density(fill = "lightblue", alpha = 0.7) +
      labs(x = plot_vars[i],
           caption = "Black = Mean, Red = Median")  
  )
  
}
```

## PCA

```{r}
pca_df <- conspiracies %>% 
  dplyr::select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory3)

pca_fit <- prcomp(pca_df,scale = TRUE)

biplot(pca_fit,
       col = c("lightgrey","red"))

pca_fit$rotation

components <- pca_fit$x[,1:3] %>% as.tibble()
```

Principal components are as follows: 

* PC1 = belief in Wuhan lab and 5G conspiracies  
* PC2 = disbelief in all three origin theories, but especially strong disbelief in meat market theory  
* PC3 = belief in meat market but not 5G  

```{r}
pc <- cbind(conspiracies,components)
pc$PC2 <- 0 - pc$PC2

princ_comps <- c("PC1","PC2","PC3")
pc[princ_comps] <- pc[princ_comps] %>% 
  map_df(rescale01, na.rm = TRUE)

pc %>% 
  ggplot(aes(x = PC1)) +
  geom_density()

pc %>% 
  ggplot(aes(x = PC2)) +
  geom_density()

pc %>% 
  ggplot(aes(x = PC3)) +
  geom_density()
```

## Modelling for belief in PC1

```{r}
pc1_full <- lm(PC1 ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  right +
                  ethno +
                  distrust_science + 
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_IOU_Total +
                  
                  #covid-anxiety
                  threat +
                  
                  #conspiracies
                  W1_Conspiracy_Total,
                 data = pc)

par(mfrow = c(2,2))
plot(pc1_full)
```


```{r}
summ(pc1_full, vifs = T)
plot_coefs(pc1_full)
```


## Modelling for belief in PC3

```{r}
pc3_full <- lm(PC3 ~ 
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   right +
                   ethno +
                   distrust_science + 
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news +
                   W2_INFO_5 + #social media
                   W2_INFO_9 + #family and friends
                   
                   #political-psychology variables
                   SDO +
                   RWA +
                   W2_IOU_Total +
                   
                   #covid-anxiety
                   threat +
                   
                   #conspiracies
                   W1_Conspiracy_Total,
                 data = pc)

par(mfrow = c(2,2))
plot(pc3_full)
```

```{r}
summ(pc3_full, vifs = T)
plot_coefs(pc3_full)
```

## Interaction model

```{r}
pc3_int <- lm(PC3 ~ 
                   #socio-economic variables
                   W2_Gender_binary +
                   W1_Education_binary +
                   W1_Income_2019 +
                   age_sc +
                   
                   #political and media variables
                   right +
                   ethno +
                   distrust_science + 
                   red_top_tabloid + 
                   mid_level_news + 
                   elite_news +
                   W2_INFO_5 + #social media
                   W2_INFO_9 + #family and friends
                   
                   #political-psychology variables
                   SDO +
                   #RWA +
                   W2_IOU_Total +
                   
                   # RWA and covid-anxiety interaction
                   (RWA*threat) +
                   
                   #conspiracies
                   W1_Conspiracy_Total,
                 data = pc)

par(mfrow = c(2,2))
plot(pc3_int)
```


```{r}
summ(pc3_int, vifs = TRUE)
plot_coefs(pc3_int)
```

## IHS model

```{r}
# functions for IHS transformation
ihs <- function(x, theta){  # IHS transformation
  asinh(theta * x)/theta
}

ihs_loglik <- function(theta,x){
  
  ihs <- function(x, theta){  # function to IHS transform
    asinh(theta * x)/theta
  }
  
  n <- length(x)
  xt <- ihs(x, theta)
  
  log_lik <- -n*log(sum((xt - mean(xt))^2))- sum(log(1+theta^2*x^2))
  return(log_lik)
}     
```

```{r}
best_theta <- optimize(ihs_loglik, 
                       lower = 0.00001, upper = 1e+06,
                       x = pc$PC1, 
                       maximum = TRUE)$maximum
best_theta # continues to rise indefinitely
```

```{r}
pc$PC1_ihs <- ihs(pc$PC1, best_theta)

pc %>% 
  ggplot(aes(x = PC1)) +
  geom_density()

pc %>% 
  ggplot(aes(x = PC1_ihs)) +
  geom_density()
```

```{r}
pc1_ihs <- lm(PC1_ihs ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  right +
                  ethno +
                  distrust_science + 
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_IOU_Total +
                  
                  #covid-anxiety
                  threat +
                  
                  #conspiracies
                  W1_Conspiracy_Total,
                 data = pc)

par(mfrow = c(2,2))
plot(pc1_ihs)
```

```{r}
summ(pc1_ihs, vifs = T)
plot_coefs(pc1_ihs)
coef(pc1_ihs)
```

## Social distancing

```{r}
## making a dataset of variables included in the models above
## plus DV's for social distancing and vaccination

vars <- model.matrix(pc1_full)[,-1] %>% as.data.frame() %>% names()
vars <- c(vars,"PC1","PC2","PC3","pid")
vars[1] <- str_sub(vars[1],1,str_length(vars[1])-1)
#vars[2] <- str_sub(vars[2],1,str_length(vars[2])-1)

public <- merge(
  pc %>% dplyr::select(one_of(vars)) %>% na.omit(),
  conspiracies %>% dplyr::select(pid,W2_SocialDistance10,
                                 W2_SocialDistance11,
                                 W2_SocialDistance12,
                                 W2_SocialDistance14,
                                 W2_C19_Vax_Self,
                                 W2_C19_Vax_Child),
  by = "pid", all.x = TRUE
)
```


```{r}
# social distance scale
sd_keys <- list(sd = cs(W2_SocialDistance10,
                        W2_SocialDistance11,
                        W2_SocialDistance12,
                        W2_SocialDistance14))

sd_test <- scoreItems(sd_keys, public, min = 1, max = 5)
head(sd_test$scores)
summary(sd_test$alpha)  # Scale alpha
public$social_distance <- rescale01(sd_test$scores, na.rm = TRUE)
public$social_distance <- c(public$social_distance)  # Ensure variable is numeric and not matrix class

describe(public$social_distance)
ggplot(public, aes(x = social_distance)) +
  geom_histogram(aes(y = ..density..),
                 binwidth = 0.1, colour = "black", fill = "lightblue") +
  geom_density()
```


```{r}
dist_full <- lm(social_distance ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  right +
                  ethno +
                  distrust_science + 
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_IOU_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #conspiracies
                  W1_Conspiracy_Total +
                  PC1 +
                  PC2 +
                  PC3,
                data = public)
summ(dist_full, vifs = T)
```


```{r}
par(mfrow = c(2,2))
plot(dist_full)
plot_coefs(dist_full)
```


## Multinomial model for vaccine acceptance

```{r}
pacman::p_load(nnet)

# multinomial model
vax_full <- multinom(W2_C19_Vax_Self ~ 
                  #socio-economic variables
                  W2_Gender_binary +
                  W1_Education_binary +
                  W1_Income_2019 +
                  age_sc +
                  
                  #political and media variables
                  right +
                  ethno +
                  distrust_science + 
                  red_top_tabloid + 
                  mid_level_news + 
                  elite_news +
                  W2_INFO_5 + #social media
                  W2_INFO_9 + #family and friends
                  
                  #political-psychology variables
                  SDO +
                  RWA +
                  W2_IOU_Total +
                  
                  #covid-anxiety
                  threat +
                 
                  #conspiracies
                  W1_Conspiracy_Total +
                  PC1 +
                  PC2 +
                  PC3,
                data = public)
```

```{r}
# functions to inspect multinom
z_score <- function(model){
  z <- summary(model)$coefficients/summary(model)$standard.errors
  return(z)
}

p_value <- function(model){
  z <- z_score(model)
  p <- (1 - pnorm(abs(z), 0, 1)) * 2
  return(p)
}
```

```{r}
p_value(vax_full)
```

```{r}
# table for plot of unstandardised coefficients
vax_vars <- c("distrust_science","threat","age_sc","W1_Income_2019",
              "RWA","SDO","PC1","PC2",
               "PC3","W1_Conspiracy_Total")

#vax_plots <- full_list[full_list %in% vax_vars]
#vax_plots <- vax_plots[sort(names(vax_plots))]

tidies <- tidy(vax_full) %>%
  filter(term %in% vax_vars) %>% 
  mutate(
    odds_ratio = exp(estimate),
    conf.low = estimate - std.error * qnorm(0.975),
    conf.high = estimate + std.error * qnorm(0.975),
    conf.low.exp = exp(estimate - std.error * qnorm(0.975)),
    conf.high.exp = exp(estimate + std.error * qnorm(0.975)),
    y.level = fct_recode(as.factor(y.level),
                         "No" = "2",
                         "Maybe" = "3")#,
    #term = fct_rev(fct_drop(fct_relevel(term, vax_plots))),
    #group_facet = ifelse(term %in% dispositions, 
    #                     "Dispositions",
    #                     ifelse(term %in% conspiracy, "Conspiracy",
    #                                   "Controls")),
    #term = fct_recode(term,
    #                  "Age" = "age_sc",
    #                  "Income" = "W1_Income_2019",
    #                  "COVID-19 anxiety" = "threat",
    #                  "Distrust scientists" = "distrust_science",
    #                  "RWA" = "RWA",
    #                  "SDO" = "SDO",
    #                  "Conspiracy ideation" = "W1_Conspiracy_Total",
    #                  "Meat market belief" = "conspiracy2_sc",
    #                  "Wuhan lab belief" = "conspiracy1_sc",
    #                 "5G belief" = "conspiracy3_sc")
  ) %>%
  rename(Level = y.level)  

# plotting beta coefficients
ggplot(data = tidies, 
       aes(y = term, 
           x = estimate, xmin = conf.low,
           xmax = conf.high, colour = Level)) + 
  geom_vline(xintercept = 0, linetype = 2, size = .25) +
  ggstance::geom_linerangeh(
    aes(y = term, xmin = conf.low,
        xmax = conf.high, colour = Level),
    position = ggstance::position_dodgev(height = 0.62), size = 0.8) +
  geom_point(
    aes(y = term, 
        x = estimate, colour = Level, shape = Level),
    position = ggstance::position_dodgev(height = 0.62),
    fill = "white", size = 3, stroke = 1, show.legend = TRUE) +
  scale_colour_manual(values = get_colors("CUD Bright",num.colors = 2)) +
  theme_nice(legend.pos = "right") +
  scale_shape_manual(values = c(21,22)) +
  drop_y_gridlines() +
  #facet_wrap(~group_facet, ncol = 1, scales = "free_y",
  #           strip.position = "left") +
  theme(axis.title.y = element_blank(),
        legend.margin=margin(t = 0, b = 0, unit='cm'),
        axis.title.x = element_text(size = 10),
        axis.text.y = element_text(size = 10,
                                   hjust = 1),
        panel.grid.major.x = element_line(linetype = "solid"),
  #      strip.text.x = element_text(size = 8),
        legend.position = "top",
        plot.caption = element_text(hjust = 0)) +
  labs(
    x = "Coefficient estimate: Vaccine acceptance",
    caption = "Note: Multinomial logit estimated using maximum likelihood.\nUnstardised coefficients and 95% confidence intervals presented. Numerical predictors scaled 0-1."
  ) 
```

Below is a plot of the average marginal effects for key variables.  

```{r, results = 'hide'}
pacman::p_load(margins)

# average marginal effect for "No", with bootstrap for variance
set.seed(123)
margin_no <- margins_summary(
  vax_full, category = "2",
  vce = "bootstrap"
)

# average marginal effect for "Maybe", with bootstrap for variance
set.seed(123)
margin_maybe <- margins_summary(
  vax_full, category = "3",
  vce = "bootstrap"
)
```


```{r}
# plotting average marginal effect
rbind(
  margin_no %>% as_tibble() %>% mutate(level = "No"),
  margin_maybe %>% as_tibble() %>% mutate(level = "Maybe")
) %>% 
  rename(term = factor) %>% 
  filter(term %in% vax_vars) %>%
  #mutate(
    #term = fct_rev(fct_drop(fct_relevel(term, vax_plots))),
    #group_facet = ifelse(term %in% dispositions, 
    #                     "Dispositions",
    #                     ifelse(term %in% conspiracy, "Conspiracy",
    #                                   "Controls")),
    #term = fct_recode(term,
    #                  "Age" = "age_sc",
    #                  "Income" = "W1_Income_2019",
    #                  "COVID-19 anxiety" = "threat",
    #                  "Distrust scientists" = "distrust_science",
    #                  "RWA" = "RWA",
    #                  "SDO" = "SDO",
    #                  "Conspiracy ideation" = "W1_Conspiracy_Total",
    #                  "Meat market belief" = "conspiracy2_sc",
    #                  "Wuhan lab belief" = "conspiracy1_sc",
    #                  "5G belief" = "conspiracy3_sc")
  #) %>% 
  ggplot(aes(y = term, 
           x = AME, xmin = lower,
           xmax = upper, colour = level)) + 
  geom_vline(xintercept = 0, linetype = 2, size = .25) +
  ggstance::geom_linerangeh(
    aes(y = term, xmin = lower,
        xmax = upper, colour = level),
    position = ggstance::position_dodgev(height = 0.62), size = 0.8) +
  geom_point(
    aes(y = term, 
        x = AME, colour = level, shape = level),
    position = ggstance::position_dodgev(height = 0.62),
    fill = "white", size = 3, stroke = 1, show.legend = TRUE) +
  scale_colour_manual(values = get_colors("CUD Bright",num.colors = 2)) +
  theme_nice(legend.pos = "right") +
  scale_shape_manual(values = c(21,22)) +
  drop_y_gridlines() +
  #facet_wrap(~group_facet, ncol = 1, scales = "free_y",
  #           strip.position = "left") +
  theme(axis.title.y = element_blank(),
        legend.margin=margin(t = 0, b = 0, unit='cm'),
        axis.title.x = element_text(size = 10),
        axis.text.y = element_text(size = 10,
                                   hjust = 1),
        panel.grid.major.x = element_line(linetype = "solid"),
        #strip.text.x = element_text(size = 8),
        legend.position = "top",
        plot.caption = element_text(hjust = 0)) +
  labs(
    x = "Average marginal effect: Vaccine acceptance",
    colour = "Level",
    shape = "Level",
    caption = "Note: Multinomial logit estimated using maximum likelihood method.  Bootstrapped 95% confidence intervals.\nNumerical predictors scaled 0-1."
  )
```

