---
title: "covid_conspiracies_markdown"
author: "Michael Marshall"
date: "21/10/2020"
output: github_document
---

## Loading Packages and Data

```{r, message = FALSE, warnings = FALSE}
pacman::p_load(tidyverse, stringr, ggridges, forcats, labelled, leaps)

load("COVID W1_W2_W3 Cleaned 2878.RData") # needs to be in your wd
```

## Summary and distribution of different COVID specific conspiracies

```{r}
df %>% 
  select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  map(summary)

# plotting density of different covid conspiracies
df %>% 
  select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  gather(conspiracy_code, belief, W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>%
  mutate(
    conspiracy_code = as.factor(conspiracy_code),
    conspiracy = ifelse(
      conspiracy_code == "W2_Conspiracy_Theory1",
      "Chinese lab",
      ifelse(conspiracy_code == "W2_Conspiracy_Theory2",
             "Chinese meat market",
             ifelse(conspiracy_code == "W2_Conspiracy_Theory3",
                    "5G",
                    ifelse(conspiracy_code == "W2_Conspiracy_Theory4",
                           "No worse than flu",
                           "Vitamin C treatment"))))
  ) %>% 
  ggplot(aes(x = belief, y = conspiracy, height = ..density..)) +
  geom_density_ridges(aes(fill = conspiracy,
                          rel_min_height = 0.005),
                      stat = "density",
                      #bins = 20,
                      show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2") +
  theme_ridges()
```

## Selecting variables for dataset

Sorry, this is a lot of manual code, and if you can think of a quicker way I'd be happy to use it.  I tend to prefer reducing the number of variables to just those I expect to reasonably use, which the code below aims to achieve.  

```{r, message = FALSE, warning=FALSE}
df_names <- names(df)

w2_vars <- df %>% 
  select(
    W2_Age_year:W2_Gender_binary,
    W2_Living_alone,W2_Employment,
    W2_Nationalism1,W2_Nationalism2,
    W2_Trust_Body1:W2_Newspaper_prefer11,
    W2_COVID19_anxiety:W2_TRUST_9,
    W2_Conspiracy_Theory1:W2_Conspiracy_Theory5,
    W2_LOC1:W2_DAI17,W2_IOU1:W2_IOU12,W2_Nationalism_Total,
    W2_Paranoia_Total,W2_Dep_Total,
    W2_GAD_Total,W2_Internal_Total,
    W2_Chance_Total,W2_PO_Total,
    W2_DAI_Total,W2_ProspectiveAnx_Total,
    W2_InhibitoryAnx_Total,W2_IOU_Total
    ) %>% 
  names()

w1_vars <- df %>% 
  select(
    W1_Area_residence,W1_Ethnicity,
    W1_Education:W1_Religion_binary,
    W1_Hosuing_tenure,W1_Income_2019,
    W1_C19_Infected:W1_C19_SomeoneClose_Infected_Binary,
    W1_ReligiousBelief1:W1_ReligiousBelief8_R,
    W1_CRT1:W1_CRT_test,
    W1_Voted_GenElection:W1_Political_Fiscal,
    W1_Authoritarianism1:W1_Authoritarianism5_R,
    W1_MigrantAttitudes1:W1_Conspiracy_5,
    W1_ReligiousBelief_Total,W1_Authoritarianism_Total,
    W1_Social_Dominance_Mean,W1_Social_Dominance_Total,
    W1_Conspiracy_Total
  ) %>% 
  names()
         
w3_vars <- c(
  "W3_ContactTracing",
  "W3_Smartphone",
  "W3_C19App1",
  "W3_C19App2",
  "W3_C19App3",
  "W3_C19App4"
)

vars <- c("pid",w1_vars,w2_vars,w3_vars)

mean(vars %in% df_names) # checking all variable names spelled correctly

# selecting variables
df_thin <- df %>% 
  select(one_of(vars))
```

## Cleaning dataset

The following code filters down to just those observations that have completed the battery of questions relating to COVID specific conspiracies.  It also creates a tibble counting the missing observations, which can be useful to have as an object.  

```{r}
# filtering for completed dependent variable
conspiracies <- df_thin %>% 
  filter(!is.na(W2_Conspiracy_Theory1) |
           !is.na(W2_Conspiracy_Theory2) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory3) |
           !is.na(W2_Conspiracy_Theory4) |
           !is.na(W2_Conspiracy_Theory5)) %>% 
  rename(W1_Housing_tenure = W1_Hosuing_tenure)

# function to count NAs
count_na <- function(x){
  sum(is.na(x))
}

conspiracies %>% 
  select(W2_Conspiracy_Theory1:W2_Conspiracy_Theory5) %>% 
  map_int(count_na)

missing <- tibble(
  variable = names(conspiracies),
  NAs = conspiracies %>% map_int(count_na)
)

#View(missing)
```

The code below combines the two variables on the 2019 general election into a single variable that combines whether a respondent voted, and who they voted for.  It also turns the *preferred newspaper* variables into dummy variables, as they were previously coded as *1=Yes* and everything else as *NA*.  

```{r}
# combining 2019 election variables into one, for parties and didn't votes

conspiracies <- conspiracies %>% 
  mutate(
    W1_Voted_Party_Name = to_factor(conspiracies$W1_Voted_Party,
                                    nolabel_to_na = TRUE),
    W1_Voted_GenElection_Name = to_factor(conspiracies$W1_Voted_GenElection,
                                          nolabel_to_na = TRUE),
    W1_2019_GE_Full = factor(ifelse(
      W1_Voted_GenElection_Name == "Voted.",
      as.character(W1_Voted_Party_Name),
      as.character(W1_Voted_GenElection_Name)
      )
      )
    )

# making preferred newspaper a dummy variable (i.e. replacing NA with 0)
na_to_zero <- function(x){
  x[is.na(x)] <- 0
  x <- as.numeric(x)
  return(x)
} 

paper_vars <- conspiracies %>%
  select(W2_Newspaper_prefer1:W2_Newspaper_prefer11) %>% 
  names()

conspiracies[paper_vars] <- conspiracies[paper_vars] %>% 
  map_df(na_to_zero)
```

The code below turns the a number of variables into factors that are currently stored as numeric.  And makes the value labels the levels in the factor.  

```{r}
factors <- conspiracies %>% 
  select(W1_Ethnicity:W1_EURef,
         W2_Gender:W2_Newspaper_prefer11) %>% 
  names()

for(i in seq_along(conspiracies[factors])){
  conspiracies[factors][,i] <- to_factor(
    conspiracies[factors][,i], nolabel_to_na = TRUE)
}

# unfortunately the loop doesn't work for the newspaper variables
class(conspiracies$W2_Newspaper_prefer1)

news <- conspiracies %>% 
  select(W2_Newspaper_prefer1:W2_Newspaper_prefer11) %>% 
  names()

conspiracies[news] <- conspiracies[news] %>% 
  map_df(as.factor)

conspiracies[news] %>% map_chr(class)

# the code chunk below just checks the loop only changed factor variables
conspiracies %>% count(W1_Ethnicity)
conspiracies %>% count(W1_EURef)
conspiracies %>% count(W2_Gender)
class(conspiracies$W2_Conspiracy_Theory1)
class(conspiracies$W2_Nationalism_Total)
summary(conspiracies$W1_Authoritarianism_Total)

# dropping the transgender level in gender variable as no respondents
conspiracies <- conspiracies %>% 
  mutate(W2_Gender = fct_drop(W2_Gender))
levels(conspiracies$W2_Gender)
```


## Distribution of variables

A for loop to look at distribution of potential independent variables (numeric only).  

```{r}
plot_vars <- conspiracies %>% 
  select(
    W1_Political_Scale:W1_Political_Fiscal,
    W1_ReligiousBelief_Total:W1_Conspiracy_Total,
    W2_Nationalism_Total:W2_IOU_Total
    ) %>%
  names()

for(i in seq_along(plot_vars)){
  
  x1 <- conspiracies[plot_vars][i] %>% as_vector()
  
  print(
    ggplot(data = NULL, aes(x = x1)) +
      geom_vline(aes(xintercept = mean(x1, na.rm =TRUE)), 
                 colour = "black",
                 #alpha = 0.7,
                 linetype = "dashed") +
      geom_vline(aes(xintercept = median(x1, na.rm =TRUE)), 
                 colour = "red",
                 #alpha = 0.7,
                 linetype = "dashed") +
      geom_density(fill = "lightblue", alpha = 0.7) +
      labs(x = plot_vars[i],
           caption = "Black = Mean, Red = Median")  
  )
  
}
```

## Vote in 2019 election and conspiracy belief

```{r}
conspiracies %>% 
  ggplot(aes(x = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory1),
             y = W2_Conspiracy_Theory1)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Vote in 2019 GE",
       y = "Belief in Chinese Lab Origin")

# filtering down for some of the main parties
parties <- c("UKIP",
             "Did not vote.",
             "Conservative",
             "Labour",
             "Green",
             "Scottish Nationalists",
             "Liberal Democrats")

conspiracies %>% 
  filter(W1_2019_GE_Full %in% parties) %>% 
  ggplot(aes(x = W2_Conspiracy_Theory1,
             y = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory1))) +
  geom_density_ridges(alpha = 0.7,
                      quantile_lines = TRUE,
                      quantiles = 4,
                      scale = 0.9,
                      jittered_points = TRUE,
                      vline_size = 1,
                      point_size = 0.6,
                      point_alpha = 0.6,
                      position = "raincloud") +
  labs(x = "Vote in 2019 GE",
       y = "Belief in Chinese lab origin")

# interestingly, Conservatives have relatively high belief in Chinese lab conspiracy

conspiracies %>% 
  ggplot(aes(x = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory3),
             y = W2_Conspiracy_Theory3)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Vote in 2019 GE",
       y = "Belief in 5G Origin")

conspiracies %>% 
  filter(W1_2019_GE_Full %in% parties) %>% 
  ggplot(aes(x = W2_Conspiracy_Theory3,
             y = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory3))) +
  geom_density_ridges(alpha = 0.7,
                      quantile_lines = TRUE,
                      quantiles = 4,
                      scale = 0.9,
                      jittered_points = TRUE,
                      vline_size = 1,
                      point_size = 0.6,
                      point_alpha = 0.6,
                      position = "raincloud") +
  labs(x = "Vote in 2019 GE",
       y = "Belief in 5G origin")

conspiracies %>% 
  ggplot(aes(x = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory4),
             y = W2_Conspiracy_Theory4)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Vote in 2019 GE",
       y = "Belief it is no worse than flu")

conspiracies %>% 
  filter(W1_2019_GE_Full %in% parties) %>% 
  ggplot(aes(x = W2_Conspiracy_Theory4,
             y = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory4))) +
  geom_density_ridges(alpha = 0.7,
                      quantile_lines = TRUE,
                      quantiles = 4,
                      scale = 0.9,
                      jittered_points = TRUE,
                      vline_size = 1,
                      point_size = 0.6,
                      point_alpha = 0.6,
                      position = "raincloud") +
  labs(x = "Vote in 2019 GE",
       y = "Belief it is no worse than flu")

conspiracies %>% 
  ggplot(aes(x = fct_reorder(W1_2019_GE_Full, W2_Conspiracy_Theory5),
             y = W2_Conspiracy_Theory5)) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "Vote in 2019 GE",
       y = "Belief in Vitamin C treatment")
```


## Forward stepwise model selection and linear model

```{r}
conspiracies_subset <- conspiracies %>% 
  select(W1_Ethnicity,W1_Education,
         W1_Income_2019,W1_CRT1:W1_CRT_test,
         W1_EURef:W1_Political_Fiscal,
         W1_ReligiousBelief_Total:W1_Authoritarianism_Total,
         W1_Social_Dominance_Total:W2_Age_year,W2_Gender,
         W2_Living_alone,W2_Employment,
         W2_Trust_Body1:W2_Newspaper_prefer11,
         W2_COVID19_anxiety,W2_Conspiracy_Theory1:W2_Conspiracy_Theory5,
         W2_Nationalism_Total:W2_IOU_Total,
         W1_2019_GE_Full)
```

```{r}
conspiracies_subset %>% 
  ggplot(aes(x = W2_Conspiracy_Theory1)) +
  geom_histogram(colour = "black", fill = "grey")

```

```{r}
pacman::p_load(plm)
model_matrix <- model.matrix(W2_Conspiracy_Theory1 ~ ., data = conspiracies_subset)
detect.lindep(model_matrix)
```


```{r}
reg_fit <- regsubsets(W2_Conspiracy_Theory1 ~ ., data = conspiracies_subset,
                      nvmax = 60, method = "forward")

plot(summary(reg_fit)$adjr2, type = "o")

summary(reg_fit)$adjr2

labels(coef(reg_fit, 38))
```

```{r}
# creating necessary dummy variables
conspiracies_subset$chinese <- ifelse(
  conspiracies_subset$W1_Ethnicity == "Chinese", 1, 0
)

conspiracies_subset$afro_caribbean <- ifelse(
  conspiracies_subset$W1_Ethnicity == "Afro-Caribbean", 1, 0
)

conspiracies_subset$gcse <- ifelse(
  conspiracies_subset$W1_Education == "O-Level/GCSE or similar", 1, 0
)

conspiracies_subset$diploma <- ifelse(
  conspiracies_subset$W1_Education == "Diploma", 1, 0
)

conspiracies_subset$income_25341_38740_pa <- ifelse(
  conspiracies_subset$W1_Income_2019 == "£491 - £740 per week (equals about £2,111 - £3,230 per month or £25,341 - £38,740 per year)", 1, 0
)

conspiracies_subset$income_57931_plus_pa <- ifelse(
  conspiracies_subset$W1_Income_2019 == "£1,112 or more per week (equals about £4,831 or more per month or £57,931 or more per year)", 1, 0
)

conspiracies_subset$CRT2_500_mins <- ifelse(
  conspiracies_subset$W1_CRT2 == "500 minutes", 1, 0
)

conspiracies_subset$CRT3_24_days <- ifelse(
  conspiracies_subset$W1_CRT3 == "24 days", 1, 0
)

conspiracies_subset$CRT3_12_days <- ifelse(
  conspiracies_subset$W1_CRT3 == "12 days", 1, 0
)

conspiracies_subset$CRT5_8 <- ifelse(
  conspiracies_subset$W1_CRT5 == "8", 1, 0
)

conspiracies_subset$remainer <- ifelse(
  conspiracies_subset$W1_EURef == "Voted to stay in EU", 1, 0
)

conspiracies_subset$ref_not_citizen <- ifelse(
  conspiracies_subset$W1_EURef == "Ineligible because not a UK citizen or resident", 1, 0
)

conspiracies_subset$living_alone <- ifelse(
  conspiracies_subset$W2_Living_alone == "Yes", 1, 0
)

conspiracies_subset$unemployed_corona <- ifelse(
  conspiracies_subset$W2_Employment == "Unemployed (becasue of coronavirus)",
  1, 0
)

conspiracies_subset$trust_govt_moderate <- ifelse(
  conspiracies_subset$W2_Trust_Body2 == "Trust moderately",
  1, 0
)

conspiracies_subset$trust_science_moderate <- ifelse(
  conspiracies_subset$W2_Trust_Body6 == "Trust moderately",
  1, 0
)

conspiracies_subset$dont_trust_doctors <- ifelse(
  conspiracies_subset$W2_Trust_Body7 == "Do not trust at all",
  1, 0
)

conspiracies_subset$green <- ifelse(
  conspiracies_subset$W1_2019_GE_Full == "Green", 1, 0
)

conspiracies_subset$ineligible_ge <- ifelse(
  conspiracies_subset$W1_2019_GE_Full == "Ineligible because not a UK citizen or resident", 1, 0
)

conspiracies_subset$sinn_fein <- ifelse(
  conspiracies_subset$W1_2019_GE_Full == "Sinn Féin", 1, 0
)

conspiracies_subset$ulster_unionist <- ifelse(
  conspiracies_subset$W1_2019_GE_Full == "Ulster Unionist", 1, 0
)

```


```{r}
lab_mod <- lm(W2_Conspiracy_Theory1 ~ chinese +
                afro_caribbean +
                gcse + 
                diploma +
                income_25341_38740_pa +
                income_57931_plus_pa +
                CRT2_500_mins +
                CRT3_24_days +
                CRT3_12_days +
                CRT5_8 +
                remainer +
                ref_not_citizen +
                W1_ReligiousBelief_Total +
                W1_Authoritarianism_Total +
                W1_Social_Dominance_Total +
                W1_Conspiracy_Total +
                living_alone +
                unemployed_corona +
                trust_govt_moderate +
                trust_science_moderate +
                dont_trust_doctors +
                W2_Newspaper_prefer1 +
                W2_Newspaper_prefer6 +
                W2_Newspaper_prefer9 +
                W2_COVID19_anxiety +
                W2_Conspiracy_Theory2 +
                W2_Conspiracy_Theory3 +
                W2_Conspiracy_Theory4 +
                W2_Conspiracy_Theory5 +
                W2_Nationalism_Total +
                W2_Paranoia_Total +
                W2_Internal_Total +
                W2_DAI_Total +
                W2_IOU_Total +
                green +
                ineligible_ge +
                sinn_fein +
                ulster_unionist,
              data = conspiracies_subset)

summary(lab_mod)
```

```{r}
par(mfrow = c(2,2))
plot(lab_mod)
```

```{r}
source("diagnostic_plots.R")

av_ggplot(lab_mod)
```

